---
title: "BabyView Objects Prolific Validation"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    self-contained: true
execute:
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(ggplot2)
library(scales)
library(irr)
library(here)
library(ggrepel)

OOD_CLASSES <- c("__OOD_BV_CROP__", "__OOD_SYNTHETIC__")

theme_set(
  theme_minimal(base_size = 12) +
    theme(
      plot.title    = element_text(hjust = 0.5, face = "bold", size = 13),
      plot.subtitle = element_text(hjust = 0.5, color = "gray40", size = 10),
      strip.text    = element_text(face = "bold")
    )
)
```

```{r load-data}
workers <- read.csv(here("data/prolific_validation/worker_indexes.csv")) |> filter(status == "complete") |> pull(worker_id)
df_raw <- read.csv(here("data/prolific_validation/prolific_annotations.csv")) |>
  filter(!class %in% OOD_CLASSES) |>
  mutate(
    order_index   = as.integer(order_index),
    reaction_time = as.numeric(reaction_time)
  ) |>
  mutate(
    rater = {
      long_ids <- unique(worker_id[nchar(worker_id) > 10])
      id_to_label <- setNames(
        paste0("rater", seq_along(long_ids)),
        long_ids
      )
      ifelse(nchar(worker_id) > 10, id_to_label[worker_id], NA_character_)
    }
  ) |>
  filter(!is.na(rater))

invalid <- df_raw |>
  filter(trial_type == "invalid_drawing") |>
  distinct(rater, trial_type, class)

other <- df_raw |>
  filter(trial_type != "invalid_drawing") 

annotation_count <- bind_rows(invalid, other) |>
  count(rater, trial_type)

df_filtered <- df_raw |>
  filter(worker_id %in% workers)

# Ground-truth universe: the canonical (class, filename) pairs both raters evaluated.
# Both raters saw shuffled_index == 1. Note: categories do NOT all have 25 images —
# n_total varies per category and is computed from this table.
all_annotations <- read.csv(here("data/prolific_validation/object_files.csv")) |>
  filter(!class %in% OOD_CLASSES) |>
  select(class, filename, shuffled_index) 

# True denominator per category — varies, do not assume 25
images_per_cat <- all_annotations |>
  count(class, shuffled_index, name = "n_total")

invalid_df <- df_filtered |> filter(trial_type == "invalid_drawing")
attn_df    <- df_filtered |> filter(trial_type == "attention_check")
```

# Overview

```{r overview-table}
df_filtered |>
  count(rater, trial_type) |>
  pivot_wider(names_from = trial_type, values_from = n, values_fill = 0) |>
  rename(
    Rater              = rater,
    `Invalid drawings` = invalid_drawing,
    `Attention checks` = attention_check
  ) |>
  knitr::kable(caption = "Rows per rater by trial type")

images_per_cat |>
  summarise(
    `# categories`  = n(),
    `Min images`    = min(n_total),
    `Max images`    = max(n_total),
    `Median images` = median(n_total),
    `Mean images`   = round(mean(n_total), 1)
  ) |>
  knitr::kable(caption = "Ground-truth universe summary (annotations.csv, shuffled_index == 1)")
```
we don't include any raters with >20 attention check misses.

# 1. Invalid Image Rate per Category

The denominator for each category is `n_total` from `all_annotations` — the actual number of
images in that category's ground-truth bucket, which varies across categories.

```{r invalid-rate-compute}
n_invalid_per_rater <- invalid_df |>
  group_by(rater, class) |>
  summarise(n_invalid = n_distinct(filename), .groups = "drop")

# Join true denominator; categories a rater marked 0 invalid won't appear above,
# All raters that exist in the data
raters <- df_filtered |> distinct(rater, shuffled_index)

# Full grid: every rater × every category in the annotation universe
full_grid <- raters |>
  cross_join(images_per_cat |> distinct(class)) # <-- ground truth universe

invalid_rate <- full_grid |>
  left_join(n_invalid_per_rater, by = c("rater", "class")) |>
  replace_na(list(n_invalid = 0L)) |>
  left_join(images_per_cat, by = c("class", "shuffled_index")) |>
  mutate(prop_invalid = n_invalid / n_total) 


avg_valid <- invalid_rate |>
  group_by(rater) |>
  summarise(
    mean_n    = round(mean(n_invalid), 2),
    mean_prop = round(1 - mean(prop_invalid), 3),
    sd_prop   = round(sd(prop_invalid), 3),
    shuffled_index = first(shuffled_index),
    .groups   = "drop"
  ) |>   arrange(shuffled_index)

avg_valid |>
  knitr::kable(
    caption   = "Average valid image proportion per rater first summarized within category",
    col.names = c("Rater", "Mean # invalid", "Mean proportion valid", "SD proportion valid", "Shuffled bucket")
  )
```




```{r invalid-rate-bar, fig.height=16, fig.width=11}
class_avgs_per_bucket <- invalid_rate |>
  group_by(class, shuffled_index) |>
  summarise(mean_prop = mean(prop_invalid), .groups = "drop") 
class_avgs <- class_avgs_per_bucket |>  group_by(class) |>
  summarize(mean_prop = mean(mean_prop)) 

cat_order <- class_avgs |>
  arrange(desc(mean_prop)) |>
  pull(class)

class_avgs_per_bucket |>
  mutate(class = factor(class, levels = rev(cat_order))) |>
  ggplot(aes(x = mean_prop, y = class, group = shuffled_index, fill = factor(shuffled_index))) +
  geom_col(position = position_dodge(0.7), width = 0.6, alpha = 0.85) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "firebrick", linewidth = 0.5) +
  scale_x_continuous(labels = percent_format(), limits = c(0, 1.05)) +
  scale_fill_discrete() +
  labs(
    title    = "Invalid Image Rate per Category",
    subtitle = "Dashed line = 50% threshold; denominator = actual # images per category",
    x        = "Proportion marked invalid",
    y        = NULL,
    fill     = NULL
  ) +
  theme(
    legend.position = "top",
    axis.text.y     = element_text(size = 7)
  )
```

```{r}
class_avgs_at_n <- class_avgs |>
  mutate(precision = 1 - mean_prop) |>
  arrange(desc(precision)) |>
  mutate(
    rank         = row_number(),
    cumulative_precision = cummean(precision)
  )

threshold_precision <- 0.5
threshold_precision_n <- class_avgs_at_n |> filter(precision >= threshold_precision) |> slice_max(rank) |> pull(rank)
threshold_cumulative_precision <- round(class_avgs_at_n |> filter(rank == threshold_precision_n) |> pull(cumulative_precision), 2)
ggplot(class_avgs_at_n, aes(x = rank, y = precision)) +
  geom_line(linewidth = 1, color = "steelblue") +
  geom_hline(yintercept = threshold_precision, linetype = "dashed", color = "firebrick") +
  geom_vline(xintercept = threshold_precision_n, linetype = "dashed", color = "firebrick") +
    annotate("label", x = threshold_precision_n, y = 0.42,
           label = paste0("N = ", threshold_precision_n), color = "firebrick", size = 3.5) +
  labs(title = "Mean precision per category", x = NULL, y = "Mean precision") +
  theme(axis.text.y = element_text(size = 7))

threshold   <- 0.8
threshold_cumulative <- class_avgs_at_n |> filter(cumulative_precision >= threshold) |> slice_max(rank) |> pull(rank)

ggplot(class_avgs_at_n, aes(x = rank, y = cumulative_precision)) +
  geom_line(linewidth = 1, color = "steelblue") +
  geom_point(size = 1.5, color = "steelblue") +
  geom_hline(yintercept = threshold, linetype = "dashed", color = "darkgreen") +
  geom_vline(xintercept = threshold_cumulative, linetype = "dashed", color = "darkgreen") +
  annotate("label", x = threshold_cumulative, y = 0.42,
           label = paste0("N = ", threshold_cumulative), color = "darkgreen", size = 3.5) +
  geom_hline(yintercept = threshold_cumulative_precision, linetype = "dashed", color = "firebrick") +
  geom_vline(xintercept = threshold_precision_n, linetype = "dashed", color = "firebrick") +
    annotate("label", x = threshold_precision_n, y = 0.42,
           label = paste0("N = ", threshold_precision_n), color = "firebrick", size = 3.5) +
    annotate("label", x = 20, y = threshold_cumulative_precision,
           label = paste0("all classes precision > 0.5, \n total precision = ", threshold_cumulative_precision), color = "firebrick", size = 3.5) +
  scale_y_continuous(limits = c(0.4, NA)) +
  labs(
    title = "Cumulative average precision (top N categories)",
    x     = "N categories (sorted by precision desc)",
    y     = "Cumulative precision"
  )
```


# 2. Inter-Rater Reliability (IRR)
```{r}
#
# Each shuffled_index bucket has 2–3 raters assigned exclusively to it.
# We compute all pairwise Cohen's kappa within each bucket, then average.

# Helper: all pairwise kappa for a set of rater columns in a wide df
pairwise_kappa <- function(wide_df, rater_cols) {
  pairs <- combn(rater_cols, 2, simplify = FALSE)
  map_dfr(pairs, function(p) {
    mat <- wide_df |> select(all_of(p)) |> as.matrix()
    k   <- tryCatch(kappa2(mat)$value, error = \(e) NA_real_)
    z   <- tryCatch(kappa2(mat)$statistic, error = \(e) NA_real_)
    pa  <- mean(wide_df[[p[1]]] == wide_df[[p[2]]])
    tibble(r1 = p[1], r2 = p[2], kappa = k, z = z, pct_agree = pa,
           n = nrow(wide_df))
  })
}

# ── Build per-bucket IRR data ─────────────────────────────────────────────────

bucket_irr_results <- map(1:4, function(idx) {
  
  bucket_raters <- invalid_df |>
    filter(shuffled_index == idx) |>
    distinct(rater) |>
    pull(rater)
  
  uni <- all_annotations |>
    filter(shuffled_index == idx)
  
  wide <- reduce(bucket_raters, function(df, r) {
    col  <- sym(r)
    flag <- invalid_df |>
      filter(rater == r, shuffled_index == idx) |>
      select(class, filename, shuffled_index) |>
      distinct() |>
      mutate(!!col := 1L)
    left_join(df, flag, by = c("class", "filename", "shuffled_index"))
  }, .init = uni) |>
    mutate(across(all_of(bucket_raters), \(x) replace_na(x, 0L)))
  
  bucket_irr <- pairwise_kappa(wide, bucket_raters) |>
    mutate(shuffled_index = idx)
  
  list(raters = bucket_raters, irr = bucket_irr, wide = wide)
})

# Then extract each piece:
bucket_irr <- map_dfr(bucket_irr_results, "irr")
bucket_wide <- map_dfr(bucket_irr_results, "wide")
bucket_raters <- map(bucket_irr_results, "raters")
  
# ── 2a. Overall kappa per bucket, then grand average ─────────────────────────
bucket_summary <- bucket_irr |>
  group_by(shuffled_index) |>
  summarise(
    n_pairs     = n(),
    n_images    = first(n),
    mean_kappa  = mean(kappa, na.rm = TRUE),
    mean_agree  = mean(pct_agree, na.rm = TRUE),
    .groups = "drop"
  )

grand <- bucket_summary |>
  summarise(
    shuffled_index = "Grand avg",
    n_pairs        = sum(n_pairs),
    mean_kappa     = weighted.mean(mean_kappa, n_images),  # n_images still vector here
    mean_agree     = weighted.mean(mean_agree, n_images),  # same
    n_images       = sum(n_images)                         # collapse LAST
  )

bind_rows(
  bucket_summary |> mutate(shuffled_index = as.character(shuffled_index)),
  grand
) |>
  knitr::kable(
    digits  = 3,
    caption = "Overall IRR per shuffled_index bucket (all-pairwise kappa, weighted grand avg)"
  )
```

## 2b per-category kappa
```{r}

cat_irr <- map_dfr(1:4, function(idx) {
  
  bucket_raters <- invalid_df |>
    filter(shuffled_index == idx) |>
    distinct(rater) |>
    pull(rater)
  
  uni <- all_annotations |> filter(shuffled_index == idx)
  
  wide <- reduce(bucket_raters, function(df, r) {
    col  <- sym(r)
    flag <- invalid_df |>
      filter(rater == r, shuffled_index == idx) |>
      select(class, filename, shuffled_index) |>
      distinct() |>
      mutate(!!col := 1L)
    left_join(df, flag, by = c("class", "filename", "shuffled_index"))
  }, .init = uni) |>
    mutate(across(all_of(bucket_raters), \(x) replace_na(x, 0L)))
  
  pairs <- combn(bucket_raters, 2, simplify = FALSE)
  
  map_dfr(pairs, function(p) {
    wide |>
      group_by(class) |>
      summarise(
        n_total   = n(),
        n_r1      = sum(.data[[p[1]]]),
        n_r2      = sum(.data[[p[2]]]),
        pct_agree = mean(.data[[p[1]]] == .data[[p[2]]]),
        kappa     = tryCatch(
          kappa2(cbind(.data[[p[1]]], .data[[p[2]]]))$value,
          error = \(e) NA_real_
        ),
        .groups = "drop"
      ) |>
      mutate(shuffled_index = idx, r1 = p[1], r2 = p[2])
  })
}) |> mutate(kappa= ifelse(is.na(kappa), 1, kappa))

# Average kappa per category across all pairs/buckets
kappa_per_cat_bucket <- cat_irr |>
  group_by(class, shuffled_index) |>
  summarise(
    n_total   = mean(n_total), 
    kappa     = mean(kappa, na.rm = TRUE),
    pct_agree = mean(pct_agree, na.rm = TRUE),
    n_pairs   = n(),
    .groups   = "drop"
  ) 

kappa_per_cat <- kappa_per_cat_bucket |>
  group_by(class) |>
  summarise(
    n_total   = sum(n_total),      # total images seen across all pairs
    kappa     = mean(kappa, na.rm = TRUE),
    pct_agree = mean(pct_agree, na.rm = TRUE),
    n_pairs   = sum(n_pairs), 
    .groups   = "drop"
  ) 

# Heatmap: top 10 + bottom 15
kappa_per_cat |>
  filter(!is.na(kappa), kappa != 0) |>
  { \(d) bind_rows(slice_max(d, kappa, n = 10), slice_min(d, kappa, n = 15)) }() |>
  distinct(class, .keep_all = TRUE) |>
  mutate(class = fct_reorder(class, kappa)) |>
  ggplot(aes(x = 1, y = class, fill = kappa)) +
  geom_tile(color = "white", linewidth = 0.3) +
  geom_text(aes(label = round(kappa, 2)), size = 4) +
  scale_fill_gradient2(
    low = "#D73027", mid = "white", high = "#1A9850",
    midpoint = 0, limits = c(-1, 1), name = "κ"
  ) +
  scale_x_continuous(breaks = NULL) +
  labs(
    title    = "Per-Category Cohen's κ (Top 10 & Bottom 15, avg across buckets & pairs)",
    subtitle = "Green = high agreement, Red = systematic disagreement",
    x = NULL, y = NULL
  ) +
  theme(axis.text.y = element_text(size = 14), axis.ticks = element_blank())
```

## 2c. Confusion matrix 
```{r}
# For a multi-rater confusion matrix we use each pairwise combination as a row.
bucket_irr_long <- map_dfr(1:4, function(idx) {
  
  bucket_raters <- invalid_df |>
    filter(shuffled_index == idx) |>
    distinct(rater) |>
    pull(rater)
  
  uni <- all_annotations |> filter(shuffled_index == idx)
  
  wide <- reduce(bucket_raters, function(df, r) {
    col  <- sym(r)
    flag <- invalid_df |>
      filter(rater == r, shuffled_index == idx) |>
      select(class, filename, shuffled_index) |>
      distinct() |>
      mutate(!!col := 1L)
    left_join(df, flag, by = c("class", "filename", "shuffled_index"))
  }, .init = uni) |>
    mutate(across(all_of(bucket_raters), \(x) replace_na(x, 0L)))
  
  pairs <- combn(bucket_raters, 2, simplify = FALSE)
  map_dfr(pairs, function(p) {
    wide |> transmute(r1 = .data[[p[1]]], r2 = .data[[p[2]]],
                      shuffled_index = idx)
  })
})

bucket_irr_long |>
  mutate(
    r1_label = if_else(r1 == 1L, "Invalid", "Valid"),
    r2_label = if_else(r2 == 1L, "Invalid", "Valid")
  ) |>
  count(r1_label, r2_label) |>
  group_by(r1_label) |>
  mutate(prop = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = r2_label, y = r1_label, fill = prop)) +
  geom_tile(color = "gray80", linewidth = 0.5) +
  geom_text(aes(label = paste0(n, "\n(", percent(prop, 1), ")")),
            size = 4, lineheight = 1.3) +
  scale_fill_gradient(low = "white", high = "steelblue", name = "Row\nprop.") +
  labs(
    title    = "Rater Agreement Confusion Matrix (all pairs, all buckets)",
    subtitle = "Each pairwise comparison contributes rows; row = rater in r1 role",
    x = "Rater 2 (role)", y = "Rater 1 (role)"
  ) +
  coord_fixed()
```
```{r invalid-rate-cat, fig.height=16, fig.width=11}
# ── 2d. Invalid count heatmap — per bucket ────────────────────────────────────
# Show mean invalid prop per category per bucket (averaged across raters in bucket)
invalid_prop_by_bucket <- cat_irr |>
  group_by(class, shuffled_index) |>
  summarise(
    n_total    = first(n_total),
    mean_n_inv = mean(c(n_r1, n_r2), na.rm = TRUE),   # avg across pairs
    prop       = mean_n_inv / n_total,
    .groups    = "drop"
  ) |>
  group_by(class) |>
  mutate(mean_prop = mean(prop, na.rm = TRUE)) |>
  ungroup() |>
  mutate(class = fct_reorder(class, mean_prop))

top_bottom_cats <- bind_rows(
  slice_max(distinct(invalid_prop_by_bucket, class, mean_prop), mean_prop, n = 25),
  slice_min(distinct(invalid_prop_by_bucket, class, mean_prop), mean_prop, n = 25)
) |> pull(class)

invalid_prop_by_bucket |>
  filter(class %in% top_bottom_cats) |>
  mutate(bucket_label = paste0("Bucket ", shuffled_index)) |>
  ggplot(aes(x = bucket_label, y = class, fill = prop)) +
  geom_tile(color = "white", linewidth = 0.3) +
  geom_text(aes(label = paste0(round(mean_n_inv), "/", n_total)), size = 3.5) +
  scale_fill_gradient(
    low = "#F7F7F7", high = "#D73027",
    name = "prop\ninvalid"
  ) +
  labs(
    title    = "Invalid Rate per Category per Bucket (Top & Bottom 25)",
    subtitle = "Labels = avg_n_invalid / n_total; averaged across raters within bucket",
    x = NULL, y = NULL
  ) +
  theme(axis.text.y = element_text(size = 11), axis.ticks = element_blank())
```

---

# 3. Time-Series: order_index vs. Invalid Images

## 3a. Invalid Images Over Time

```{r timeseries-invalid, fig.width=11, fig.height=5}
invalid_per_block <- invalid_df |>
  group_by(rater, order_index) |>
  summarise(n_invalid = n_distinct(filename), .groups = "drop")

attn_per_block <- attn_df |>
  group_by(rater, order_index) |>
  summarise(n_attn = n(), .groups = "drop")

ggplot(invalid_per_block, aes(x = order_index, y = n_invalid, color = rater)) +
  geom_point(alpha = 0.45, size = 1.5) +
  geom_smooth(method = "loess", span = 0.35, se = TRUE, linewidth = 1.1, alpha=0.2) +
  scale_color_manual(values = c("Rater 1" = "#4393C3", "Rater 2" = "#D6604D")) +
  labs(
    title    = "Invalid Images per Block Over Time",
    subtitle = "Each point = one category block; ribbon = loess ± SE",
    x = "Order index (block number)", y = "# images marked invalid", color = NULL
  ) +
  theme(legend.position = "top")
```


investigating the hard attention check fails 
```{r}
attn_df |> group_by(rater, order_index, class, filename) |> summarize(n = n()) |> filter(n >= 4)
```
table was hard, updated.


# output dfs/summary
## per class
```{r}
per_class <- class_avgs_at_n |>
  transmute(class, precision = round(precision,4), rank, cumulative_precision=round(cumulative_precision, 4), n_images = 100)

per_bucket <- class_avgs_per_bucket |>
  transmute(class, shuffled_index, precision = round(1 - mean_prop, 4)) |>
  pivot_wider(names_from=shuffled_index, values_from = precision, names_prefix = "precision_bucket_") 

irr_per_class <- kappa_per_cat |>
  transmute(class, kappa = round(kappa,4), pct_agree = round(pct_agree, 4), n_pair_raters = n_pairs)
  
per_class_data <- per_class |> left_join(per_bucket) |> left_join(irr_per_class)
write.csv(per_class_data, here("data/prolific_validation/per_class_validation_data.csv"))
```

## per file
```{r}
per_file_precision <- bucket_wide |> pivot_longer(starts_with("rater"), names_to="rater", values_to="rater_code") |> filter(!is.na(rater_code)) |> group_by(filename, class) |>
  summarize(precision = round(mean(rater_code), 4), raters = n())
write.csv(per_file_precision, here("data/prolific_validation/per_file_precision_data.csv"))
```

## summary stats
```{r}
per_class_data |> summarize(precision = round(mean(precision),4), `Average Cohen's kappa across raters` = round(mean(kappa),4), `Percent agreement between raters` = round(mean(pct_agree),4), `Number of total images` = sum(n_images)) |> knitr::kable(caption = "Summary stats")
```


does precision correlate with reliability?
```{r}
cor.test(per_class_data$precision, per_class_data$kappa)
```
it does not.