---
title: "Developmental Trajectory Top 8 Densest — Stats & Visualization (R)"
author: "From notebook 12 outputs"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: flatly
execute:
  warning: false
  message: false
---

## Setup and data paths

Data are CSVs exported by notebook 12 (`12_developmental_trajectory_top8_densest.ipynb`). Paths are relative to this file. **Render from** `analysis/individual_analyses/` so that `developmental_trajectory_top8_densest/` is found (e.g. `quarto render developmental_trajectory_top8_densest_stats.qmd`).

```{r setup}
#| label: setup
library(tidyverse)
library(broom)
library(broom.mixed)

# Optional: for mixed-effects models and bootstrap CIs
if (requireNamespace("lme4", quietly = TRUE)) library(lme4)
if (requireNamespace("boot", quietly = TRUE)) library(boot)

data_dir <- "developmental_trajectory_top8_densest"
# If rendering from repo root or elsewhere, adjust:
if (!dir.exists(data_dir)) data_dir <- file.path("analysis", "individual_analyses", data_dir)
stopifnot("Data directory not found" = dir.exists(data_dir))
```

## Load CSVs

```{r load-data}
#| label: load-data
mm       <- read_csv(file.path(data_dir, "month_to_month_correlations.csv"), show_col_types = FALSE)
yv       <- read_csv(file.path(data_dir, "youngest_vs_later_month_correlations.csv"), show_col_types = FALSE)
mm_top50 <- read_csv(file.path(data_dir, "month_to_month_correlations_top50.csv"), show_col_types = FALSE)
yv_top50 <- read_csv(file.path(data_dir, "youngest_vs_later_month_correlations_top50.csv"), show_col_types = FALSE)
fixed     <- read_csv(file.path(data_dir, "subject_fixed_categories_all.csv"), show_col_types = FALSE)
smooth_mm <- read_csv(file.path(data_dir, "smooth_trajectory_month_to_month.csv"), show_col_types = FALSE)
smooth_yv <- read_csv(file.path(data_dir, "smooth_youngest_vs_later.csv"), show_col_types = FALSE)
hours     <- read_csv(file.path(data_dir, "hours_per_subject_age_mo.csv"), show_col_types = FALSE)

# Standard error -> approximate 95% CI (assuming normality of correlation scale)
mm       <- mm       %>% mutate(ci_lo = correlation - 1.96 * cor_se, ci_hi = correlation + 1.96 * cor_se)
yv       <- yv       %>% mutate(ci_lo = correlation - 1.96 * cor_se, ci_hi = correlation + 1.96 * cor_se)
mm_top50 <- mm_top50 %>% mutate(ci_lo = correlation - 1.96 * cor_se, ci_hi = correlation + 1.96 * cor_se)
yv_top50 <- yv_top50 %>% mutate(ci_lo = correlation - 1.96 * cor_se, ci_hi = correlation + 1.96 * cor_se)

n_subj <- n_distinct(mm$subject_id)
```

- **Month-to-month**: `r nrow(mm)` rows (consecutive-month RDM correlations).
- **Youngest vs later**: `r nrow(yv)` rows (youngest-month RDM vs each later month).
- **Subjects**: `r n_subj` (top 8 densest).

## Descriptive summary

```{r summary}
#| label: summary
# By subject: mean correlation and age range
mm %>%
  group_by(subject_id) %>%
  summarise(
    n_transitions = n(),
    mean_corr = mean(correlation),
    sd_corr = sd(correlation),
    age_min = min(age_from),
    age_max = max(age_to),
    .groups = "drop"
  ) %>%
  knitr::kable(digits = 3)
```

## Statistical tests

### 1. Month-to-month: does correlation depend on age?

We fit a linear mixed model: correlation ~ age_midpoint + (1 | subject_id) to test the effect of age while accounting for repeated measures per subject.

```{r test-mm-age}
#| label: test-mm-age
fit_mm <- lm(correlation ~ age_midpoint, data = mm)
summary(fit_mm)
confint(fit_mm)
```

**With random subject intercept** (if `lme4` available):

```{r test-mm-mixed}
#| label: test-mm-mixed
if (requireNamespace("lme4", quietly = TRUE)) {
  fit_mm_mixed <- lme4::lmer(correlation ~ age_midpoint + (1 | subject_id), data = mm)
  summary(fit_mm_mixed)
  cat("\n--- 95% CI (profile) ---\n")
  print(confint(fit_mm_mixed, method = "Wald"))
} else {
  cat("lme4 not installed; using OLS only.\n")
}
```

### 2. Youngest vs later: does correlation with youngest month decrease with age gap?

Predict correlation from `age_compared` (and optionally `age_youngest`). Clustering by subject.

```{r test-yv-age}
#| label: test-yv-age
fit_yv <- lm(correlation ~ age_compared, data = yv)
summary(fit_yv)
confint(fit_yv)
```

```{r test-yv-mixed}
#| label: test-yv-mixed
if (requireNamespace("lme4", quietly = TRUE)) {
  fit_yv_mixed <- lme4::lmer(correlation ~ age_compared + (1 | subject_id), data = yv)
  summary(fit_yv_mixed)
  cat("\n--- 95% CI (Wald) ---\n")
  print(confint(fit_yv_mixed, method = "Wald"))
}
```

### 3. All-categories vs top-50 (month-to-month)

Compare mean correlation (or trajectory) between full set and top-50. We have separate files; we can compare at overlapping (subject, age) points.

```{r compare-all-vs-top50}
#| label: compare-all-vs-top50
# Join month-to-month all vs top50 on subject_id, age_from, age_to
both_mm <- mm %>%
  select(subject_id, age_from, age_to, age_midpoint, correlation, cor_se) %>%
  rename(corr_all = correlation, cor_se_all = cor_se) %>%
  inner_join(
    mm_top50 %>% select(subject_id, age_from, age_to, correlation, cor_se) %>%
      rename(corr_top50 = correlation, cor_se_top50 = cor_se),
    by = c("subject_id", "age_from", "age_to")
  )
# Paired t-test: is top50 systematically higher?
with(both_mm, t.test(corr_top50, corr_all, paired = TRUE))
# Mean difference with 95% CI
both_mm %>%
  mutate(diff = corr_top50 - corr_all) %>%
  summarise(
    mean_diff = mean(diff),
    se_diff = sd(diff) / sqrt(n()),
    ci_lo = mean_diff - 1.96 * se_diff,
    ci_hi = mean_diff + 1.96 * se_diff
  ) %>%
  knitr::kable(digits = 4)
```

## Visualizations with confidence intervals

### 4. Month-to-month: correlation vs age (raw + smooth with CI)

Raw points with pointwise 95% CI (from `cor_se`); smooth trajectory uses precomputed `smooth_trajectory_month_to_month.csv` which has `pred`, `ci_lo`, `ci_hi` for "overall".

```{r fig-mm-raw}
#| label: fig-mm-raw
#| fig-cap: "Consecutive-month RDM correlation vs age midpoint. Points = one per (subject, transition); error bars = 95% CI from cor_se."
#| fig-width: 8
#| fig-height: 5
p_mm_raw <- ggplot() +
  geom_errorbar(
    data = mm,
    aes(x = age_midpoint, y = correlation, ymin = ci_lo, ymax = ci_hi, color = subject_id),
    width = 0.15, linewidth = 0.3, alpha = 0.6
  ) +
  geom_point(data = mm, aes(x = age_midpoint, y = correlation, color = subject_id), size = 1.5, alpha = 0.8) +
  geom_line(data = mm, aes(x = age_midpoint, y = correlation, color = subject_id), linewidth = 0.4, alpha = 0.7) +
  scale_color_viridis_d(option = "turbo", end = 0.9) +
  labs(x = "Age midpoint (months)", y = "RDM correlation (consecutive months)", color = "Subject") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "right")
p_mm_raw
```

```{r fig-mm-smooth}
#| label: fig-mm-smooth
#| fig-cap: "Overall smooth trajectory with 95% CI (from notebook 12 smooth fit)."
#| fig-width: 8
#| fig-height: 5
smooth_overall_mm <- smooth_mm %>% filter(subject_id == "overall")
ggplot() +
  geom_ribbon(
    data = smooth_overall_mm,
    aes(x = age, ymin = ci_lo, ymax = ci_hi),
    fill = "steelblue", alpha = 0.35
  ) +
  geom_line(data = smooth_overall_mm, aes(x = age, y = pred), color = "steelblue", linewidth = 1.1) +
  geom_point(data = mm, aes(x = age_midpoint, y = correlation), alpha = 0.25, size = 1) +
  labs(x = "Age (months)", y = "RDM correlation (consecutive months)") +
  theme_minimal(base_size = 12)
```

### 5. Youngest vs later month: correlation vs age compared (raw + smooth with CI)

```{r fig-yv-raw}
#| label: fig-yv-raw
#| fig-cap: "Correlation of each month's RDM with the youngest month's RDM. Points = one per (subject, age_compared); error bars = 95% CI."
#| fig-width: 8
#| fig-height: 5
p_yv_raw <- ggplot() +
  geom_errorbar(
    data = yv,
    aes(x = age_compared, y = correlation, ymin = ci_lo, ymax = ci_hi, color = subject_id),
    width = 0.15, linewidth = 0.3, alpha = 0.6
  ) +
  geom_point(data = yv, aes(x = age_compared, y = correlation, color = subject_id), size = 1.5, alpha = 0.8) +
  geom_line(data = yv, aes(x = age_compared, y = correlation, color = subject_id), linewidth = 0.4, alpha = 0.7) +
  scale_color_viridis_d(option = "turbo", end = 0.9) +
  labs(x = "Age (months)", y = "Correlation with youngest month RDM", color = "Subject") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "right")
p_yv_raw
```

```{r fig-yv-smooth}
#| label: fig-yv-smooth
#| fig-cap: "Overall smooth trajectory (youngest vs later) with 95% CI."
#| fig-width: 8
#| fig-height: 5
smooth_overall_yv <- smooth_yv %>% filter(subject_id == "overall")
ggplot() +
  geom_ribbon(
    data = smooth_overall_yv,
    aes(x = age, ymin = ci_lo, ymax = ci_hi),
    fill = "darkorange", alpha = 0.35
  ) +
  geom_line(data = smooth_overall_yv, aes(x = age, y = pred), color = "darkorange", linewidth = 1.1) +
  geom_point(data = yv, aes(x = age_compared, y = correlation), alpha = 0.25, size = 1) +
  labs(x = "Age (months)", y = "Correlation with youngest month RDM") +
  theme_minimal(base_size = 12)
```

### 6. All-categories vs top-50 (month-to-month) with CI

```{r fig-compare-mm}
#| label: fig-compare-mm
#| fig-cap: "Month-to-month correlation: all categories vs top-50. Mean trajectory with 95% CI by age bin."
#| fig-width: 8
#| fig-height: 5
# Aggregate by age_midpoint: mean and CI across subjects
summ_all <- mm %>%
  group_by(age_midpoint) %>%
  summarise(
    mean_corr = mean(correlation),
    se = sd(correlation) / sqrt(n()),
    ci_lo = mean_corr - 1.96 * se,
    ci_hi = mean_corr + 1.96 * se,
    set = "all",
    .groups = "drop"
  )
summ_top50 <- mm_top50 %>%
  group_by(age_midpoint) %>%
  summarise(
    mean_corr = mean(correlation),
    se = sd(correlation) / sqrt(n()),
    ci_lo = mean_corr - 1.96 * se,
    ci_hi = mean_corr + 1.96 * se,
    set = "top50",
    .groups = "drop"
  )
bind_rows(summ_all, summ_top50) %>%
  ggplot(aes(x = age_midpoint, y = mean_corr, color = set, fill = set)) +
  geom_ribbon(aes(ymin = ci_lo, ymax = ci_hi), alpha = 0.25, color = NA) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_color_manual(values = c(all = "steelblue", top50 = "coral2")) +
  scale_fill_manual(values = c(all = "steelblue", top50 = "coral2")) +
  labs(x = "Age midpoint (months)", y = "Mean RDM correlation", color = "Category set", fill = "Category set") +
  theme_minimal(base_size = 12)
```

### 7. Fixed category set size per subject

```{r fig-fixed-cats}
#| label: fig-fixed-cats
#| fig-cap: "Number of common categories used for each subject (fixed set across age)."
fixed %>%
  ggplot(aes(x = reorder(subject_id, -n_fixed_categories), y = n_fixed_categories, fill = subject_id)) +
  geom_col(show.legend = FALSE) +
  scale_fill_viridis_d(option = "turbo", end = 0.9) +
  labs(x = "Subject", y = "Number of fixed categories") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Session info

```{r session-info}
#| label: session-info
sessionInfo()
```
