---
title: "object_detections_glmers_bll"
author: "Bria Long"
date: "2025-04-09"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the libraries
library(tidyverse)
library(babyviewr)
library(lubridate)
library(ggthemes)
library(kableExtra)
library(here)
library(ggrepel)
library(ggpubr)
library(lme4)
library(broom.mixed)
library(effects)
```

# Load intermediate dataframe
This comes from the first few steps in
```{r}
object_counts_by_age = read_csv(file=here::here('frame_data/preprocessed_object_detections.csv')) %>%
  filter(!is.na(num_frames)) # we don't have data in every age bin
```


# Mixed-effect models


```{R}
for_glmer <- object_counts_by_age %>%
  mutate(num_not_detected = num_frames - num_detected) %>%
  mutate(class_name = as.factor(class_name), subject_id = as.factor(subject_id)) 
```

Run your main age model, scaling for age, and with the maximal random effects structure justified by your data
```{r}
age_model = glmer(data=for_glmer, cbind(num_detected, num_not_detected) ~ scale(age_mo) + (scale(age_mo) | subject_id) +   (scale(age_mo) | class_name), family='binomial')

age_model_no_class_slopes = glmer(data=for_glmer, cbind(num_detected, num_not_detected) ~ scale(age_mo) + (scale(age_mo) | subject_id) +  (1| class_name), family='binomial')

age_model_no_sub_slopes = glmer(data=for_glmer, cbind(num_detected, num_not_detected) ~ scale(age_mo) + (1 | subject_id) +  (scale(age_mo)| class_name), family='binomial')
```

```{R}
anova(age_model, age_model_no_class_slopes)
```

```{r}
anova(age_model, age_model_no_sub_slopes)

```

```{r}
age_model_proportion= glmer(data=for_glmer %>% mutate(prop_detected = num_detected/num_frames), prop_detected ~ scale(age_mo) + (scale(age_mo) | subject_id) + (scale(age_mo) | class_name), weights =num_frames, family='binomial')

summary(age_model_proportion)
```

```{r}
ranef_df <- as.data.frame(ranef(age_model))
head(ranef_df)
```

```{r}
positive_changes_across_age <- ranef_df %>%
  filter(grpvar=='class_name') %>%
  filter(term=='scale(age_mo)') %>%
  slice_max(order_by=condval, n=10)

neg_changes_across_age <- ranef_df %>%
  filter(grpvar=='class_name') %>%
  filter(term=='scale(age_mo)') %>%
  slice_max(order_by=-condval, n=10)
```


```{R}
library(MuMIn)
r.squaredGLMM(age_model)

r.squaredGLMM(age_model_proportion)
```

# Bria tries something else 
Now, let's just look at figuring out if we can correlate the distributions (we can try spearman rank correlations, which is better tha pearson's since it's non-linear data )



Now, get counts of how often the objects appeared
```{r}
by_subject <- object_counts_by_age %>%
  filter(age_mo<12) %>%
  group_by(subject_id, class_name) %>% # now group by our main variables
  summarize(num_detected = sum(num_detected), total_frames_by_sub = sum(num_frames))%>%
  mutate(num_not_detected = total_frames_by_sub - num_detected) %>%
  mutate(prop_detected = num_detected/total_frames_by_sub)

by_subject_frames <- object_counts_by_age %>%
  group_by(subject_id) %>% # now group by our main variables
  summarize(total_frames_by_sub = sum(num_frames))

frames_by_age <- object_counts_by_age %>%
  group_by(age_mo) %>% # now group by our main variables
  summarize(total_frames_by_age = sum(num_frames))
  
```

Get classes where 2/3 of subjects don't have detections, we might want to exclude them to see how correlations change later...
```{r}
mostly_zeros <- by_subject %>%
  filter(prop_detected==0) %>%
  group_by(class_name) %>%
  summarize(num_subs_zeros = length(unique(subject_id))) %>%
  arrange(-num_subs_zeros) %>%
  filter(num_subs_zeros>20)
  
```


OK, get a wide dataframe so you can make correlations across subjects
```{R}
by_subject_wide <- by_subject |>
  # filter(! class_name %in% mostly_zeros$class_name) %>%
  select(subject_id, class_name, prop_detected) |>
  pivot_wider(names_from = class_name, values_from = prop_detected, values_fill=0)

cor_matrix <- by_subject_wide %>%
  column_to_rownames("subject_id") %>%
  t() %>%
  cor(use = "pairwise.complete.obs", method='spearman')
```

Convert to tidy format and compute average correlation per subject
```{r}
avg_corr_by_subject <- as.data.frame(cor_matrix) %>%
  rownames_to_column("subject_id") %>%
  pivot_longer(-subject_id, names_to = "other_subject", values_to = "correlation") %>%
  filter(subject_id != other_subject) %>%  # exclude self-correlation
  group_by(subject_id) %>%
  summarise(avg_correlation = mean(correlation, na.rm = TRUE), sd_correlation = sd(correlation)) %>%
  arrange(desc(avg_correlation)) %>%
  left_join(by_subject_frames)
```

OK, do subjects with more data just have higher correlations with each other?
```{R}
cor.test(avg_corr_by_subject$total_frames_by_sub, avg_corr_by_subject$avg_correlation)
```

To some extent, I think so?
```{r}
qplot(avg_corr_by_subject$total_frames_by_sub, avg_corr_by_subject$avg_correlation)
```

## Now same thing by age
```{R}
by_age_wide <- object_counts_by_age |>
  group_by(age_mo, class_name) |>
  summarize(num_detected = sum(num_detected)) %>%
left_join(frames_by_age) %>%  
  mutate(prop_detected = num_detected / total_frames_by_age) %>%
  select(-num_detected, -total_frames_by_age) %>%
  pivot_wider(names_from = class_name, values_from = prop_detected, values_fill=0)

cor_matrix_age <- by_age_wide %>%
  column_to_rownames("age_mo") %>%
  t() %>%
  cor(use = "pairwise.complete.obs", method='spearman')
```

Convert to tidy format and compute average correlation per age
```{r}
avg_corr_by_age <- as.data.frame(cor_matrix_age) %>%
  rownames_to_column("age_mo") %>%
  pivot_longer(-age_mo, names_to = "other_age", values_to = "correlation") %>%
  filter(age_mo != other_age) %>%  # exclude self-age correlation
  group_by(age_mo) %>%
  summarise(avg_correlation = mean(correlation, na.rm = TRUE), sd_correlation = sd(correlation)) %>%
  arrange(desc(age_mo)) %>%
  mutate(age_mo = as.numeric(age_mo)) %>%
  left_join(frames_by_age)
```

Whew this looks kinda like the data density plot.
```{r}
ggplot(data=avg_corr_by_age, aes(x=as.numeric(age_mo), y=avg_correlation, size=total_frames_by_age)) +
  geom_point(alpha=.2) + 
  ylab('Average spearman correlation between age bins')
```
