---
title: "Object–name cooccurrence statistics"
format: 
  html:
    toc: true
    theme: flatly
---

```{r, message=F}
library(tidyverse)
library(lubridate)
library(here)
library(ggcorrplot)
library(GGally)
library(udpipe)
theme_set(theme_classic())
# ud_dl <- udpipe_download_model("english")
ud_mod <- udpipe_load_model(here("english-ewt-ud-2.5-191206.udpipe"))

knitr::opts_chunk$set(
  message=F
)
```

```{r}
WINDOW_THRESHOLD = 5
```


## Data loading
```{r}
merged_filtered <- read_csv(here("data", "merged_cooccurrences_filtered.csv")) |> 
  mutate(confidence = as.numeric(confidence))
```

```{r}
merged_cleaned <- merged_filtered |> 
  group_by(superseded_gcp_name_feb25, token_id, utterance_id, utterance, token_num, token, 
           token_start_time, token_end_time, speaker) |> 
  summarise(first_frame = min(original_frame_path),
            min_window = min(min_diff),
            .groups = "drop")
```

Reading in other annotations
```{r}
all_objects <- read_csv(here("data", "merged_objects.csv"))
all_trans <- read_csv(here("data", "merged_trans.csv")) # NOTE: not in GitHub due to size
```

Transcript parsing
```{r, eval=F}
ud_text <- all_trans |> 
  group_by(superseded_gcp_name_feb25, utterance_id, utterance) |> 
  summarise(text = paste(token, collapse = "\n"),
            .groups = "drop")

ud_annotated <- udpipe_annotate(ud_mod, x = ud_text$text, tokenizer = "vertical") |> 
  as_tibble()

all_trans_annotated <- all_trans |> 
  arrange(superseded_gcp_name_feb25, utterance_id) |> 
  cbind(ud_annotated |> select(-token_id, -token))

write_csv(all_trans_annotated, "merged_trans_annotated.csv")
```

```{r}
all_trans_annotated <- read_csv(here("data", "merged_trans_annotated.csv"))
```

```{r}
merged_cleaned_annotated <- merged_cleaned |> 
  left_join(all_trans_annotated, 
            by = join_by(superseded_gcp_name_feb25, 
                         utterance_id, 
                         token_id,
                         utterance,
                         token,
                         token_num, 
                         token_start_time, 
                         token_end_time, 
                         speaker)) |> 
  filter(upos == "NOUN")
```

AoAs
```{r}
eng_aoas <- read_csv(here("data", "eng_aoas.csv")) |> 
  select(-intercept, -slope) |> 
  pivot_wider(names_from = "measure",
              values_from = "aoa") |> 
  mutate(item_definition = item_definition |>
           str_replace_all(c(
             " \\(object\\)" = "",
             " \\(animal\\)" = "",
             " \\(food\\)" = "",
             " \\(beverage\\)" = "",
             " \\(not beverage\\)" = "",
             "soda/pop" = "soda",
             "tissue/kleenex" = "tissue"
           ))) |> 
  group_by(item_definition) |>
  summarise(produces = min(produces, na.rm = T),
            understands = min(understands, na.rm = T),
            .groups = "drop") |> 
  mutate(understands = ifelse(is.infinite(understands), NA, understands))
```

```{r}
merged_plot_annotated <- merged_cleaned_annotated |> 
  filter(min_window <= WINDOW_THRESHOLD) |>
  group_by(token) |> 
  summarise(cooccurrences = n(),
            .groups = "drop") |> 
  left_join(eng_aoas, by = join_by(token == item_definition))
```

Summaries
```{r}
obj_summary <- all_objects |> 
  group_by(class_name) |> 
  summarise(n_frames = sum(n_frames),
            mean_area = sum(n_detections * mean_area) / sum(n_detections),
            n_detections = sum(n_detections),
            .groups = "drop")
tok_summary <- all_trans_annotated |> 
  filter(upos == "NOUN") |> 
  group_by(superseded_gcp_name_feb25, token) |> 
  summarise(n_counts = n(),
            .groups = "drop") |> 
  group_by(token) |> 
  summarise(n_counts = sum(n_counts),
            n_videos = n(),
            .groups = "drop")
```

```{r}
merged_all <- merged_plot_annotated |> 
  left_join(obj_summary, by = join_by(token == class_name)) |> 
  left_join(tok_summary, by = join_by(token == token)) |> 
  rename(frames_with_object = n_frames,
         token_count = n_counts)
```

## Visualisations and models
```{r}
ggplot(merged_all,
       aes(x = log(cooccurrences), y = log(frames_with_object))) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Log number of cooccurrences",
       y = "Log number of frames with object")
```

```{r}
lm(produces ~ scale(log(cooccurrences)) + scale(log(frames_with_object)) + scale(log(token_count)), 
   data = merged_all) |> 
  summary()
```

What about PMI?
```{r}
TOTAL_FRAMES = 3163675
merged_all_info <- merged_all |> 
  mutate(pmi = log(cooccurrences * TOTAL_FRAMES / (frames_with_object * token_count * 2 * WINDOW_THRESHOLD)),
         pmi = ifelse(is.infinite(pmi), NA, pmi)) # |> 
  # left_join(eng_aoas |> select(item_definition, measure, aoa) |> 
  #             pivot_wider(names_from = measure, values_from = aoa) |> 
  #             mutate(item_definition = item_definition |> 
  #                      str_replace_all(" \\(\\w+\\)", "")) |> 
  #             group_by(item_definition) |> 
  #             summarise(produces = min(produces, na.rm = T),
  #                       understands = min(understands, na.rm = T)) |> 
  #             suppressWarnings() |> 
  #             mutate(understands = ifelse(is.infinite(understands), NA, understands)),
  #           by = join_by(token == item_definition)) |> 
  # select(-aoa)
```

```{r}
merged_all_info_log <- merged_all_info |> 
  mutate(across(c(cooccurrences,
                  frames_with_object,
                  token_count),
                log)) |> 
  select(token,
         cooccurrences,
         frames_with_object,
         token_count,
         pmi,
         aoa_prod = produces,
         aoa_comp = understands)

merged_cor <- cor(merged_all_info_log |> select(-token),
                  use = "pairwise.complete.obs")
ggcorrplot(merged_cor)
```

```{r, warning=F}
ggpairs(merged_all_info_log |> select(-token), progress = FALSE)
```

```{r}
lm(produces ~ scale(pmi) + scale(log(frames_with_object)) + scale(log(token_count)), 
   data = merged_all_info) |> 
  summary()
```

```{r}
lm(understands ~ scale(pmi) + scale(log(frames_with_object)) + scale(log(token_count)), 
   data = merged_all_info) |> 
  summary()
```

## Clerkin & Smith analysis
Things to replicate:

- Relative proportion of things that are shared between visual objs and obj names
- Using their "whole-mealtime" window: 
  - In the future: cut up into 15min chunks (~=11.2min mean mealtime); for now just use videos
  - Prop of chunks with object in view / name / cooccurrence
  - Duration of objects that cooccur with name
  - Number of naming instances when cooccurring with object
  - They had a "pattern" over individual categories analysis; I think PMI is a better indicator of this

### Q1. How do viz object freqs correlate with naming freqs?
```{r}
ggplot(merged_all_info,
       aes(x = log(token_count), y = log(frames_with_object))) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Log number of tokens",
       y = "Log number of frames with object")
```

```{r}
cor(merged_all_info$token_count,
    merged_all_info$frames_with_object,
    use = "pairwise.complete.obs",
    method = "spearman")
```

Answer: Not very. Note that this isn't due solely to lower freq items!

### Q2. What are the proportions of videos that contain objects/namings/cooccurrences?

```{r}
# objects are already summarised
objects_by_vid <- all_objects

tokens_by_vid <- all_trans_annotated |> 
  filter(upos == "NOUN", token %in% all_objects$class_name) |> 
  group_by(superseded_gcp_name_feb25, token) |> 
  summarise(n_counts = n(),
            .groups = "drop")

cooccurrences_by_vid <- merged_cleaned_annotated |> 
  group_by(superseded_gcp_name_feb25, token) |> 
  summarise(cooccurrences = n(),
            .groups = "drop")
```

```{r}
TOTAL_N_VIDEOS = n_distinct(all_objects$superseded_gcp_name_feb25)

object_vid_props <- objects_by_vid |> 
  group_by(class_name) |> 
  summarise(vids_with_object = n(),
            .groups = "drop") |> 
  mutate(prop_vids_with_objects = vids_with_object / TOTAL_N_VIDEOS) |> 
  rename(token = class_name)

token_vid_props <- tokens_by_vid |>
  group_by(token) |> 
  summarise(vids_with_token = n(),
            .groups = "drop") |> 
  mutate(prop_vids_with_tokens = vids_with_token / TOTAL_N_VIDEOS)

cooc_vid_props <- cooccurrences_by_vid |> 
  group_by(token) |> 
  summarise(vids_with_cooc = n(),
            .groups = "drop") |> 
  mutate(prop_vids_with_cooc = vids_with_cooc / TOTAL_N_VIDEOS)

# We follow C&S by having our canonical sort order be the rank order of videos in which the object is in view.
vid_props <- object_vid_props |> 
  left_join(token_vid_props, by = join_by(token)) |> 
  left_join(cooc_vid_props, by = join_by(token)) |> 
  mutate(prop_vids_with_objects = ifelse(is.na(prop_vids_with_objects), 0, prop_vids_with_objects),
         prop_vids_with_tokens = ifelse(is.na(prop_vids_with_tokens), 0, prop_vids_with_tokens),
         prop_vids_with_cooc = ifelse(is.na(prop_vids_with_cooc), 0, prop_vids_with_cooc)) |> 
  arrange(desc(vids_with_object))
```

For visual clarity we obtain the most frequent 25 viz objects and names, as in C&S
```{r}
top_objects <- vid_props |> 
  arrange(desc(vids_with_object)) |> 
  slice(1:25) |> 
  pull(token)

top_names <- vid_props |> 
  arrange(desc(vids_with_token)) |> 
  slice(1:25) |> 
  pull(token)

top_all <- union(top_objects, top_names)
```

Viz
```{r}
ggplot(vid_props |> filter(token %in% top_all),
       aes(x = prop_vids_with_objects, y = reorder(token, -vids_with_object))) +
  geom_col() +
  coord_cartesian(xlim = c(0, 1)) +
  labs(x = "Proportion of videos with object in view", y = "Object") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
ggplot(vid_props |> filter(token %in% top_all),
       aes(x = prop_vids_with_tokens, y = reorder(token, -vids_with_object))) +
  geom_col() +
  coord_cartesian(xlim = c(0, 1)) +
  labs(x = "Proportion of videos with named object", y = "Object") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
ggplot(vid_props |> filter(token %in% top_all),
       aes(x = prop_vids_with_cooc, y = reorder(token, -vids_with_object))) +
  geom_col() +
  coord_cartesian(xlim = c(0, 1)) +
  labs(x = "Proportion of videos with object–name cooccurrences", y = "Object") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))
```

### Q3. When objects and names do cooccur, what are the visual/naming statistics?

```{r}
vid_full <- cooccurrences_by_vid |> 
  left_join(objects_by_vid, 
            by = join_by(superseded_gcp_name_feb25, token == class_name)) |>
  left_join(tokens_by_vid,
            by = join_by(superseded_gcp_name_feb25, token)) |> 
  left_join(object_vid_props,
            by = join_by(token))
```

```{r}
obj_medians <- vid_full |> filter(token %in% top_all) |> 
                  group_by(token) |> 
                  summarise(median_dur = median(n_frames, na.rm = T) / 60,
                            .groups = "drop") |> 
  left_join(object_vid_props,
            by = join_by(token))

ggplot(vid_full |> filter(token %in% top_all),
       aes(x = n_frames / 60, y = reorder(token, -vids_with_object))) +
  geom_jitter(alpha = .1) +
  geom_crossbar(aes(x = median_dur, xmin = median_dur, xmax = median_dur), 
                data = obj_medians,
                color = "cornflowerblue") +
  labs(x = "Duration of object in view (min)", y = "Object")
```

```{r}
tok_medians <- vid_full |> filter(token %in% top_all) |> 
                  group_by(token) |> 
                  summarise(median_namings = median(n_counts, na.rm = T),
                            .groups = "drop") |> 
  left_join(object_vid_props,
            by = join_by(token))

ggplot(vid_full |> filter(token %in% top_all),
       aes(x = n_counts, y = reorder(token, -vids_with_object))) +
  geom_jitter(alpha = .1) +
  geom_crossbar(aes(x = median_namings, xmin = median_namings, xmax = median_namings), 
                data = tok_medians,
                color = "cornflowerblue") +
  labs(x = "Number of object namings", y = "Object")
```

### Q4. Are there different patterns of object–name cooccurrences?
We operationalise this by showing PMI
```{r}
ggplot(merged_all_info |> 
         filter(token %in% top_all) |> 
         left_join(object_vid_props,
            by = join_by(token)),
       aes(x = pmi, y = reorder(token, -vids_with_object))) +
  geom_col() +
  labs(x = "Pointwise mutual information", y = "Object")
```

```{r}
merged_info_top <- merged_all_info |> 
  arrange(desc(pmi)) |> 
  slice(1:20)
merged_info_bot <- merged_all_info |> 
  arrange(pmi) |> 
  slice(1:20)
merged_info_plot <- bind_rows(merged_info_top, merged_info_bot)

ggplot(merged_info_plot,
       aes(x = pmi, y = reorder(token, -pmi))) +
  geom_col() +
  facet_grid(ifelse(pmi > 0, "Highest PMI", "Lowest PMI") |> 
               factor(levels = c("Lowest PMI", "Highest PMI")) ~ ., scales = "free") +
  labs(x = "Pointwise mutual information", y = "Object")
```

