---
title: "object_detection_analysis_ccn_mar25"
author: "Jane Yang"
date: "2025-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the libraries
library(tidyverse)
library(babyviewr)
library(lubridate)
library(ggthemes)
library(kableExtra)
library(here)
library(ggrepel)
library(ggpubr)
library(lme4)
library(broom.mixed)
library(effects)
```

# Load BV metadata from airtable
```{r}
# Load the data
participants <- babyviewr::get_participant_data(include_demographics = TRUE)
recordings <- babyviewr::get_main_recording_data(include_luna = TRUE)
```

```{r}
d <- left_join(recordings, 
                      participants |>
                        filter(dataset %in% c("BV-main")) |>
                        select(-dataset), by = "subject_id") |>
  filter(dataset == "BV-main") |>
  group_by(subject_id) |>
  arrange(date_time) |>
  mutate(age = date(date_time) - date_birth_rounded, 
         cumulative_hrs = cumsum(duration_hrs), 
         age_mo = floor(as.numeric(age)/30.3))


ggplot(filter(d, dataset == "BV-main"), 
       aes(x = age/30.3, y = cumulative_hrs, col = subject_id)) + 
  geom_point(alpha= .1) + 
  scale_color_discrete(guide = FALSE) + 
  theme_few() + 
  xlab("Age (months)") + 
  ylab("Cumulative hours of data")
```

```{r}
age_density <- d |>
  group_by(age_mo, dataset) |>
  summarise(n = n(), 
            n_participants = n_distinct(subject_id), 
            n_hours = sum(duration_hrs))

ggplot(age_density, aes(x = age_mo, y = n_hours, fill = dataset)) + 
  geom_bar(stat = "identity") + 
  xlab("Age (months)") + 
  ylab("Total hours of data") + 
  scale_fill_solarized() +
  theme_few()
```

# Load Object Detection Data (super large file!)
```{r}
objects <- read_csv(here::here("frame_data/allframes_1fps.csv")) 
# objects_joined <- inner_join(objects, d, by = c("superseded_gcp_name_feb25"))

# any(recordings$superseded_gcp_name_feb25 == "00510002_2024-08-12_2_dfc73374a", na.rm=TRUE)

# objects$superseded_gcp_name_feb25[!(objects$superseded_gcp_name_feb25 %in% recordings$superseded_gcp_name_feb25)]

colnames(objects)
```

# Merge the object detection file with the recording data
```{r}
objects_joined <- inner_join(objects, d, by = c("superseded_gcp_name_feb25"))
head(objects_joined)
```
```{r}
paste("Number of frames with detections:")
nrow(objects_joined |> distinct(frame_id, superseded_gcp_name_feb25))
```
# Load CDI words
```{r}
cdi_words <- read_csv(here::here("cdi_words.csv"))
```

# Seperate the objects_joined dataframe into animated, small, and big objects
```{r}
# check what categories each CDI word belongs to
cdi_categories <- cdi_words %>%
  select(uni_lemma, is_animated, is_small_obj, is_big_obj)

# join objects_joined with cdi categories based on class_name matching uni_lemma
objects_joined_with_categories <- objects_joined %>%
  left_join(cdi_categories, by = c("class_name" = "uni_lemma"))

# separate into categories
animated_objects <- objects_joined_with_categories %>%
  filter(is_animated == 1) %>%
  select(superseded_gcp_name_feb25, frame_id, time_in_extended_iso, class_name, 
         subject_id, age_mo, confidence)

small_objects <- objects_joined_with_categories %>%
  filter(is_small_obj == 1) %>%
  select(superseded_gcp_name_feb25, frame_id, time_in_extended_iso, class_name, 
         subject_id, age_mo, confidence)

big_objects <- objects_joined_with_categories %>%
  filter(is_big_obj == 1) %>%
  select(superseded_gcp_name_feb25, frame_id, time_in_extended_iso, class_name, 
         subject_id, age_mo, confidence)
```

```{r}
colnames(small_objects)
# colnames(objects_joined)
```

```{r}
# Define the plot_top_objects function
plot_top_objects <- function(data, category_name, threshold) {
  # Create plot for top 10 objects
  p <- data %>%
    head(10) %>%
    ggplot(aes(x = reorder(class_name, -n_occurrences), 
               y = n_occurrences, 
               fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = sprintf("n=%d\nconf=%.2f", 
                                 n_occurrences, 
                                 mean_confidence)),
              vjust = -0.5,
              size = 3) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    theme_few() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "Class Name",
         y = "Number of Unique Frame Occurrences",
         title = sprintf("Top 10 %s Objects (Confidence ≥ %.1f)", 
                        category_name, 
                        threshold),
         fill = "Mean\nConfidence")
  
  # Save the plot
  ggsave(here::here(sprintf("analysis_plots/%s_objects_top10_conf%.1f.png", 
                           tolower(category_name), 
                           threshold)),
         p,
         width = 12,
         height = 8)
  
  return(p)
}
```

## Generate summary stats and plots for each confidence threshold
```{r}
confidence_thresholds <- c(0.3, 0.5, 0.7)

# First, ensure frame_id is included in the initial selection
objects_joined_with_categories <- objects_joined_with_categories %>%
  select(superseded_gcp_name_feb25, frame_id, time_in_extended_iso, class_name, subject_id, age_mo, 
         confidence, is_animated, is_small_obj, is_big_obj)

# And modify the distinct statement in our functions to use both frame_id and time_in_extended_iso
generate_summary_stats <- function(objects_df, threshold) {
  # First deduplicate objects within the same frame
  objects_filtered <- objects_df %>%
    filter(confidence >= threshold) %>%
    # Keep only one instance of each object per frame using both identifiers
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE)
  
  # Process each category separately to reduce memory usage
  animated <- objects_filtered %>%
    filter(is_animated == 1) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),  # Now counts unique frame occurrences
      n_participants = n_distinct(subject_id),
      mean_confidence = mean(confidence)
    ) %>%
    arrange(desc(n_occurrences))
  
  small <- objects_filtered %>%
    filter(is_small_obj == 1) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),
      n_participants = n_distinct(subject_id),
      mean_confidence = mean(confidence)
    ) %>%
    arrange(desc(n_occurrences))
  
  big <- objects_filtered %>%
    filter(is_big_obj == 1) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),
      n_participants = n_distinct(subject_id),
      mean_confidence = mean(confidence)
    ) %>%
    arrange(desc(n_occurrences))
  
  list(
    animated = animated,
    small = small,
    big = big
  )
}

# Process one threshold at a time
for (threshold in confidence_thresholds) {
  cat(sprintf("\n=== Processing threshold %.1f ===\n", threshold))
  
  stats <- generate_summary_stats(objects_joined_with_categories, threshold)
  
  # Plot and save results for this threshold
  plot_top_objects(stats$animated, "Animated", threshold)
  plot_top_objects(stats$small, "Small", threshold)
  plot_top_objects(stats$big, "Big", threshold)
  
  # Print summaries
  cat(sprintf("\n=== Results for confidence threshold %.1f ===\n", threshold))
  
  cat("\nAnimated Objects (top 10):\n")
  print(head(stats$animated, 10))
  
  cat("\nSmall Objects (top 10):\n")
  print(head(stats$small, 10))
  
  cat("\nBig Objects (top 10):\n")
  print(head(stats$big, 10))
  
  # Save the statistics to files
  write_csv(stats$animated, 
            here::here(sprintf("analysis_plots/animated_stats_conf%.1f.csv", threshold)))
  write_csv(stats$small, 
            here::here(sprintf("analysis_plots/small_stats_conf%.1f.csv", threshold)))
  write_csv(stats$big, 
            here::here(sprintf("analysis_plots/big_stats_conf%.1f.csv", threshold)))
  
  # Clear some memory
  rm(stats)
  gc()
}

# Modified comparison plot function to read from saved files
plot_threshold_comparison <- function(category_type) {
  # Read data for each threshold from saved files
  comparison_data <- do.call(rbind, lapply(confidence_thresholds, function(threshold) {
    stats <- read_csv(here::here(sprintf("analysis_plots/%s_stats_conf%.1f.csv", 
                                       category_type, threshold)))
    stats$threshold <- threshold
    stats
  }))
  
  # Get top 10 objects (based on highest threshold)
  top_objects <- comparison_data %>%
    filter(threshold == max(threshold)) %>%
    arrange(desc(n_occurrences)) %>%
    head(10) %>%
    pull(class_name)
  
  # Create comparison plot
  comparison_data %>%
    filter(class_name %in% top_objects) %>%
    ggplot(aes(x = threshold, y = n_occurrences, color = class_name)) +
    geom_line() +
    geom_point() +
    theme_few() +
    theme(legend.position = "right") +
    xlab("Confidence Threshold") +
    ylab("Number of Occurrences") +
    ggtitle(sprintf("%s Objects: Occurrences vs Confidence Threshold", 
                    str_to_title(category_type)))
  
  ggsave(here::here(sprintf("analysis_plots/%s_threshold_comparison.png", 
                           category_type)), 
         width = 12, 
         height = 8)
}

# Generate comparison plots
plot_threshold_comparison("animated")
plot_threshold_comparison("small")
plot_threshold_comparison("big")
```
# Check consistency and variability across age/participant

# 1. Data Preparation: Create age bins and identify valid participants
```{r data_prep}
# Create age bins
objects_joined_with_categories <- objects_joined_with_categories %>%
  mutate(age_bin = case_when(
    age_mo >= 6 & age_mo < 12 ~ "06-12 months",
    age_mo >= 12 & age_mo < 18 ~ "12-18 months",
    age_mo >= 18 ~ "18-24+ months",
    TRUE ~ "Other"
  ))

# Function to get participants with sufficient data
get_valid_participants <- function(data, min_frames = 1000) {
  data %>%
    group_by(subject_id) %>%
    summarise(frame_count = n_distinct(frame_id)) %>%
    filter(frame_count >= min_frames) %>%
    pull(subject_id)
}

# Get list of valid participants
valid_participants <- get_valid_participants(objects_joined_with_categories)
```

# 2. Define function for generating participant and age-specific statistics
```{r stats_function}
# Modified summary stats function to handle participant and age bin grouping
generate_participant_age_stats <- function(objects_df, threshold, participant_id, age_bin_val) {
  objects_filtered <- objects_df %>%
    filter(confidence >= threshold,
           subject_id == participant_id,
           age_bin == age_bin_val) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE)
  
  # Process each category
  list(
    animated = objects_filtered %>%
      filter(is_animated == 1) %>%
      group_by(class_name) %>%
      summarise(
        n_occurrences = n(),
        mean_confidence = mean(confidence)
      ) %>%
      arrange(desc(n_occurrences)),
    
    small = objects_filtered %>%
      filter(is_small_obj == 1) %>%
      group_by(class_name) %>%
      summarise(
        n_occurrences = n(),
        mean_confidence = mean(confidence)
      ) %>%
      arrange(desc(n_occurrences)),
    
    big = objects_filtered %>%
      filter(is_big_obj == 1) %>%
      group_by(class_name) %>%
      summarise(
        n_occurrences = n(),
        mean_confidence = mean(confidence)
      ) %>%
      arrange(desc(n_occurrences))
  )
}
```

# 3. Define plotting function for participant-specific visualizations
```{r plot_function}
# Modified plotting function to include participant and age bin information
plot_top_objects_by_participant <- function(data, category_name, threshold, participant_id, age_bin_val) {
  if (nrow(data) == 0) {
    return(NULL)  # Return NULL if no data for this combination
  }
  
  p <- data %>%
    head(10) %>%
    ggplot(aes(x = reorder(class_name, -n_occurrences), 
               y = n_occurrences, 
               fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = sprintf("n=%d\nconf=%.2f", 
                                 n_occurrences, 
                                 mean_confidence)),
              vjust = -0.5,
              size = 3) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    theme_few() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "Class Name",
         y = "Number of Unique Frame Occurrences",
         title = sprintf("Top 10 %s Objects\nParticipant: %s, Age: %s\n(Confidence ≥ %.1f)", 
                        category_name,
                        participant_id,
                        age_bin_val,
                        threshold),
         fill = "Mean\nConfidence")
  
  # Save the plot
  ggsave(here::here(sprintf("analysis_plots/by_participant/%s_objects_top10_conf%.1f_%s_%s.png", 
                           tolower(category_name),
                           threshold,
                           participant_id,
                           gsub(" ", "_", age_bin_val))),
         p,
         width = 12,
         height = 8)
  
  return(p)
}
```

# 4. Generate plots for each participant, age bin, and threshold
```{r generate_plots}
# Create directory for participant-specific plots
dir.create(here::here("analysis_plots/by_participant"), showWarnings = FALSE)

# Process data for each participant, age bin, and threshold
for (participant in valid_participants) {
  cat(sprintf("\nProcessing participant: %s\n", participant))
  
  for (age_bin in c("06-12 months", "12-18 months", "18-24+ months")) {
    for (threshold in confidence_thresholds) {
      stats <- generate_participant_age_stats(objects_joined_with_categories, 
                                           threshold, 
                                           participant, 
                                           age_bin)
      
      # Generate plots if data exists
      if (nrow(stats$animated) > 0) {
        plot_top_objects_by_participant(stats$animated, "Animated", threshold, participant, age_bin)
      }
      if (nrow(stats$small) > 0) {
        plot_top_objects_by_participant(stats$small, "Small", threshold, participant, age_bin)
      }
      if (nrow(stats$big) > 0) {
        plot_top_objects_by_participant(stats$big, "Big", threshold, participant, age_bin)
      }
    }
  }
}
```

# 5. Generate summary statistics for data availability
```{r data_summary}
# Generate summary of data availability
data_availability <- objects_joined_with_categories %>%
  group_by(subject_id, age_bin) %>%
  summarise(
    n_frames = n_distinct(frame_id, superseded_gcp_name_feb25),
    n_unique_objects = n_distinct(class_name),
    mean_confidence = mean(confidence),
    .groups = 'drop'  # Add this to avoid grouping warning
  ) %>%
  filter(subject_id %in% valid_participants)

# Print data availability summary
print(data_availability)

# Create a heatmap of data availability
ggplot(data_availability, 
       aes(x = age_bin, y = subject_id, fill = n_frames)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "steelblue") +
  theme_few() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Data Availability by Participant and Age",
       x = "Age Bin",
       y = "Participant ID",
       fill = "Number of\nFrames")

ggsave(here::here("analysis_plots/by_participant/data_availability_heatmap.png"),
       width = 10,
       height = 8)
```

# 6. Generate combined top 10 visualization across categories
```{r combined_top10}
# Function to get category type(s)
get_category_types <- function(class_name, cdi_categories) {
  types <- cdi_categories %>%
    filter(uni_lemma == class_name) %>%
    select(is_animated, is_small_obj, is_big_obj)
  
  # If no matching row found, return "Other"
  if (nrow(types) == 0) return("Other")
  
  # Take the first row (should only be one match anyway)
  types <- types[1,]
  
  category_types <- c()
  if (types$is_animated[1] == 1) category_types <- c(category_types, "Animated")
  if (types$is_small_obj[1] == 1) category_types <- c(category_types, "Small")
  if (types$is_big_obj[1] == 1) category_types <- c(category_types, "Big")
  
  if (length(category_types) == 0) return("Other")
  paste(category_types, collapse = " & ")
}

# Get overall top 10 objects for each confidence threshold
generate_combined_top10 <- function(threshold) {
  # Get all objects with their counts and confidence, excluding "person"
  all_objects <- objects_joined_with_categories %>%
    filter(confidence >= threshold,
           class_name != "person") %>%  # Add exclusion for "person"
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    ) %>%
    arrange(desc(n_occurrences)) %>%
    head(10)
  
  # Add category information
  all_objects %>%
    mutate(
      category_type = sapply(class_name, get_category_types, cdi_categories),
      class_name = reorder(class_name, n_occurrences)
    )
}

# Generate and plot for each threshold
for (threshold in confidence_thresholds) {
  top10_data <- generate_combined_top10(threshold) %>%
    # Ensure proper descending order
    arrange(desc(n_occurrences)) %>%
    mutate(class_name = factor(class_name, levels = class_name))
  
  p <- ggplot(top10_data, 
              aes(x = class_name, 
                  y = n_occurrences, 
                  fill = category_type)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = sprintf("n=%d\nconf=%.2f", 
                                 n_occurrences, 
                                 mean_confidence)),
              vjust = -0.1,
              size = 3) +
    scale_fill_brewer(palette = "Set2") +
    theme_few() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "right"
    ) +
    labs(
      x = "Class Name",
      y = "Number of Unique Frame Occurrences",
      title = sprintf("Top 10 Objects by Category Type (Confidence ≥ %.1f)", threshold),
      fill = "Category Type"
    )
  
  # Save the plot
  ggsave(here::here(sprintf("analysis_plots/combined_top10_conf%.1f.png", threshold)),
         p,
         width = 14,  # Increased width to accommodate legend
         height = 8)
  
  # Print summary
  cat(sprintf("\nCategory distribution for threshold %.1f:\n", threshold))
  print(table(top10_data$category_type))
}

# Function to get top 10 objects across all subjects first
get_overall_top10 <- function(data, threshold) {
  data %>%
    filter(confidence >= threshold,
           class_name != "person") %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      total_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    ) %>%
    arrange(desc(total_occurrences)) %>%
    head(10) %>%
    pull(class_name)
}

# Create faceted plot function for age bins
plot_top10_by_age <- function(threshold) {
  # Get overall top 10 objects
  top10_objects <- get_overall_top10(objects_joined_with_categories, threshold)
  
  # Get per-age-bin counts for these objects
  age_counts <- objects_joined_with_categories %>%
    filter(confidence >= threshold,
           class_name %in% top10_objects,
           age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, age_bin, .keep_all = TRUE) %>%
    group_by(age_bin, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),  # Added this to track participant counts
      .groups = 'drop'
    ) %>%
    # Ensure all age bins have all top 10 objects (including 0 counts)
    complete(age_bin, class_name, 
            fill = list(n_occurrences = 0, 
                       mean_confidence = 0, 
                       n_participants = 0))
  
  # Create the faceted plot
  p <- ggplot(age_counts, 
              aes(x = reorder(class_name, -n_occurrences), 
                  y = n_occurrences,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = sprintf("n=%d\np=%d", 
                                 n_occurrences,
                                 n_participants)),  # Show both counts and number of participants
              vjust = -0.5,
              size = 3) +
    facet_wrap(~age_bin) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    theme_few() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      strip.text = element_text(size = 10),
      plot.title = element_text(size = 12)
    ) +
    labs(
      x = "Class Name",
      y = "Number of Unique Frame Occurrences",
      title = sprintf("Top 10 Objects Across Age Groups (Confidence ≥ %.1f)", threshold),
      subtitle = "n = number of occurrences, p = number of participants",
      fill = "Mean\nConfidence"
    )
  
  # Save the plot
  ggsave(here::here(sprintf("analysis_plots/top10_by_age_conf%.1f.png", threshold)),
         p,
         width = 15,
         height = 8)
  
  return(p)
}

# Generate plots for each threshold
for (threshold in confidence_thresholds) {
  plot_top10_by_age(threshold)
}
```

# Proportional analysis without person and picture
# =============================================
```{r}

# Get overall top 10 objects first (excluding person and picture)
get_overall_top10_prop <- function(data) {
  data %>%
    filter(!class_name %in% c("person", "picture")) %>%  # Exclude both person and picture
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      total_occurrences = n(),
      .groups = 'drop'
    ) %>%
    arrange(desc(total_occurrences)) %>%
    head(10) %>%
    pull(class_name)
}

# 1. Overall top 10 plot (proportion of total frames)
generate_combined_top10_prop <- function() {
  # Get total number of frames
  total_frames <- objects_joined_with_categories %>%
    distinct(superseded_gcp_name_feb25, frame_id) %>%
    nrow()
  
  # Get all objects with their proportions
  all_objects <- objects_joined_with_categories %>%
    filter(!class_name %in% c("person", "picture")) %>%  # Exclude both person and picture
    distinct(superseded_gcp_name_feb25, frame_id, class_name, subject_id, age_bin, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),
      proportion = n()/total_frames,
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),
      .groups = 'drop'
    ) %>%
    arrange(desc(proportion))
  
  # Add category information
  all_objects %>%
    mutate(
      category_type = sapply(class_name, get_category_types, cdi_categories),
      class_name = reorder(class_name, proportion)
    )
}

# 2. Plot by subject (proportion of each subject's frames)
plot_top10_by_subject_prop <- function() {
  # Get overall top 10 objects
  top10_objects <- get_overall_top10_prop(objects_joined_with_categories)
  
  # Get total frames per subject
  subject_totals <- objects_joined_with_categories %>%
    distinct(superseded_gcp_name_feb25, frame_id, subject_id) %>%
    group_by(subject_id) %>%
    summarise(total_frames = n())
  
  # Get per-subject proportions for these objects
  subject_props <- objects_joined_with_categories %>%
    filter(class_name %in% top10_objects) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, subject_id, .keep_all = TRUE) %>%
    group_by(subject_id, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    ) %>%
    left_join(subject_totals, by = "subject_id") %>%
    mutate(proportion = n_occurrences/total_frames) %>%
    complete(subject_id, class_name, 
             fill = list(n_occurrences = 0, 
                        mean_confidence = 0, 
                        proportion = 0))
  
  p <- ggplot(subject_props, 
              aes(x = reorder(class_name, proportion),
                  y = proportion,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    facet_wrap(~subject_id) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    scale_y_continuous(labels = scales::percent) +
    coord_flip() +
    theme_few() +
    theme(
      axis.text.y = element_text(hjust = 0),
      strip.text = element_text(size = 8),
      plot.title = element_text(size = 12)
    ) +
    labs(
      y = "Proportion of Frames",
      x = "Category",
      title = "Top 10 Objects Across Subjects",
      subtitle = "Percentage of frames containing each object",
      fill = "Mean\nConfidence"
    )
  
  ggsave(here::here("analysis_plots/top10_by_subject_proportions_nolabels.png"),
         p,
         width = 15,
         height = 10)
  
  return(p)
}

# 3. Plot by age (proportion of frames in each age bin)
plot_top10_by_age_prop <- function() {
  # Get overall top 10 objects
  top10_objects <- get_overall_top10_prop(objects_joined_with_categories)
  
  # Get total frames per age bin
  age_totals <- objects_joined_with_categories %>%
    filter(age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, age_bin) %>%
    group_by(age_bin) %>%
    summarise(total_frames = n())
  
  # Get per-age-bin proportions for these objects
  age_props <- objects_joined_with_categories %>%
    filter(class_name %in% top10_objects,
           age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, age_bin, .keep_all = TRUE) %>%
    group_by(age_bin, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),
      .groups = 'drop'
    ) %>%
    left_join(age_totals, by = "age_bin") %>%
    mutate(proportion = n_occurrences/total_frames) %>%
    complete(age_bin, class_name, 
             fill = list(n_occurrences = 0, 
                        mean_confidence = 0, 
                        n_participants = 0,
                        proportion = 0))
  
  p <- ggplot(age_props, 
              aes(x = reorder(class_name, proportion),
                  y = proportion,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    facet_wrap(~age_bin) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    scale_y_continuous(labels = scales::percent) +
    coord_flip() +
    theme_few() +
    theme(
      axis.text.y = element_text(hjust = 0),
      strip.text = element_text(size = 10),
      plot.title = element_text(size = 12)
    ) +
    labs(
      y = "Proportion of Frames",
      x = "Category",
      title = "Top 10 Objects Across Age Groups",
      subtitle = "Percentage of frames containing each object",
      fill = "Mean\nConfidence"
    )
  
  ggsave(here::here("analysis_plots/top10_by_age_proportions_nolabels.png"),
         p,
         width = 15,
         height = 8)
  
  return(p)
}

# Generate all three plots
top10_data_prop <- generate_combined_top10_prop()

# Overall top 10 proportional plot
p1_prop <- ggplot(top10_data_prop, 
            aes(x = reorder(class_name, proportion),
                y = proportion, 
                fill = category_type)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  theme_few() +
  theme(
    axis.text.y = element_text(hjust = 0),
    legend.position = "right"
  ) +
  labs(
    y = "Proportion of Frames",
    x = "Category",
    title = "Top 10 Objects by Category Type",
    subtitle = "Percentage of frames containing each object",
    fill = "Category Type"
  )

ggsave(here::here("analysis_plots/combined_top10_proportions_nolabels.png"),
       p1_prop,
       width = 14,
       height = 8)

# Generate by-subject proportional plot
p2_prop <- plot_top10_by_subject_prop()

# Generate by-age proportional plot
p3_prop <- plot_top10_by_age_prop()

# Print summary
print("Category distribution in top 10 (proportional analysis):")
print(table(top10_data_prop$category_type))
```

# New code block for Top 50 Analysis
# =================================

```{r}
# Get overall top 50 objects
get_overall_top50_prop <- function(data) {
  data %>%
    filter(!class_name %in% c("person", "picture")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      total_occurrences = n(),
      .groups = 'drop'
    ) %>%
    arrange(desc(total_occurrences)) %>%
    head(50) %>%
    pull(class_name)
}

# 1. Overall top 50 plot (proportion of total frames)
generate_combined_top50_prop <- function() {
  total_frames <- objects_joined_with_categories %>%
    distinct(superseded_gcp_name_feb25, frame_id) %>%
    nrow()
  
  all_objects <- objects_joined_with_categories %>%
    filter(!class_name %in% c("person", "picture")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),
      proportion = n()/total_frames,
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),
      .groups = 'drop'
    ) %>%
    arrange(desc(proportion)) %>%
    head(50)
  
  all_objects %>%
    mutate(
      category_type = sapply(class_name, get_category_types, cdi_categories),
      class_name = reorder(class_name, proportion)
    )
}

# 2. Plot by subject (proportion of each subject's frames)
plot_top50_by_subject_prop <- function() {
  # Get overall top 50 objects
  top50_objects <- get_overall_top50_prop(objects_joined_with_categories)
  
  # Get total frames per subject
  subject_totals <- objects_joined_with_categories %>%
    distinct(superseded_gcp_name_feb25, frame_id, subject_id) %>%
    group_by(subject_id) %>%
    summarise(total_frames = n())
  
  # Get per-subject proportions for these objects
  subject_props <- objects_joined_with_categories %>%
    filter(class_name %in% top50_objects) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, subject_id, .keep_all = TRUE) %>%
    group_by(subject_id, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    ) %>%
    left_join(subject_totals, by = "subject_id") %>%
    mutate(proportion = n_occurrences/total_frames) %>%
    complete(subject_id, class_name, 
             fill = list(n_occurrences = 0, 
                        mean_confidence = 0, 
                        proportion = 0))
  
  p <- ggplot(subject_props, 
              aes(x = reorder(class_name, proportion),
                  y = proportion,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    facet_wrap(~subject_id) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    scale_y_continuous(labels = scales::percent) +
    coord_flip() +
    theme_few() +
    theme(
      axis.text.y = element_text(hjust = 0, size = 7),  # Decreased to 7
      axis.text.x = element_text(size = 7),  # Decreased to 7
      strip.text = element_text(size = 10),
      plot.title = element_text(size = 12)
    ) +
    labs(
      y = "Proportion of Frames",
      x = "Category",
      title = "Top 50 Objects Across Subjects",
      subtitle = "Percentage of frames containing each object",
      fill = "Mean\nConfidence"
    )
  
  ggsave(here::here("analysis_plots/top50_by_subject_proportions_nolabels.png"),
         p,
         width = 22,
         height = 25)
  
  return(p)
}

# 3. Plot by age (proportion of frames in each age bin)
plot_top50_by_age_prop <- function() {
  top50_objects <- get_overall_top50_prop(objects_joined_with_categories)
  
  age_totals <- objects_joined_with_categories %>%
    filter(age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, age_bin) %>%
    group_by(age_bin) %>%
    summarise(total_frames = n())
  
  age_props <- objects_joined_with_categories %>%
    filter(class_name %in% top50_objects,
           age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, age_bin, .keep_all = TRUE) %>%
    group_by(age_bin, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),
      .groups = 'drop'
    ) %>%
    left_join(age_totals, by = "age_bin") %>%
    mutate(proportion = n_occurrences/total_frames) %>%
    complete(age_bin, class_name, 
             fill = list(n_occurrences = 0, 
                        mean_confidence = 0, 
                        n_participants = 0,
                        proportion = 0))
  
  p <- ggplot(age_props, 
              aes(x = reorder(class_name, proportion),
                  y = proportion,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    facet_wrap(~age_bin) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    scale_y_continuous(labels = scales::percent) +
    coord_flip() +
    theme_few() +
    theme(
      axis.text.y = element_text(hjust = 0, size = 14),
      axis.text.x = element_text(size = 12),
      strip.text = element_text(size = 12),
      plot.title = element_text(size = 12)
    ) +
    labs(
      y = "Proportion of Frames",
      x = "Category",
      title = "Top 50 Objects Across Age Groups",
      subtitle = "Percentage of frames containing each object",
      fill = "Mean\nConfidence"
    )
  
  ggsave(here::here("analysis_plots/top50_by_age_proportions_nolabels.png"),
         p,
         width = 17,
         height = 20)
  
  return(p)
}

# Generate all three proportional plots for top 50
top50_data_prop <- generate_combined_top50_prop()

# Overall top 50 proportional plot - BIGGER labels
p1_prop_50 <- ggplot(top50_data_prop, 
            aes(x = reorder(class_name, proportion),
                y = proportion, 
                fill = category_type)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  theme_few() +
  theme(
    axis.text.y = element_text(hjust = 0, size = 14),
    axis.text.x = element_text(size = 12),
    legend.position = "right"
  ) +
  labs(
    y = "Proportion of Frames",
    x = "Category",
    title = "Top 50 Objects by Category Type",
    subtitle = "Percentage of frames containing each object",
    fill = "Category Type"
  )

ggsave(here::here("analysis_plots/combined_top50_proportions_nolabels.png"),
       p1_prop_50,
       width = 16,
       height = 20)

# Plot by subject - SMALLER labels
plot_top50_by_subject_prop <- function() {
  # Get overall top 50 objects
  top50_objects <- get_overall_top50_prop(objects_joined_with_categories)
  
  # Get total frames per subject
  subject_totals <- objects_joined_with_categories %>%
    distinct(superseded_gcp_name_feb25, frame_id, subject_id) %>%
    group_by(subject_id) %>%
    summarise(total_frames = n())
  
  # Get per-subject proportions for these objects
  subject_props <- objects_joined_with_categories %>%
    filter(class_name %in% top50_objects) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, subject_id, .keep_all = TRUE) %>%
    group_by(subject_id, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    ) %>%
    left_join(subject_totals, by = "subject_id") %>%
    mutate(proportion = n_occurrences/total_frames) %>%
    complete(subject_id, class_name, 
             fill = list(n_occurrences = 0, 
                        mean_confidence = 0, 
                        proportion = 0))
  
  p <- ggplot(subject_props, 
              aes(x = reorder(class_name, proportion),
                  y = proportion,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    facet_wrap(~subject_id) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    scale_y_continuous(labels = scales::percent) +
    coord_flip() +
    theme_few() +
    theme(
      axis.text.y = element_text(hjust = 0, size = 7),  # Decreased to 7
      axis.text.x = element_text(size = 7),  # Decreased to 7
      strip.text = element_text(size = 10),
      plot.title = element_text(size = 12)
    ) +
    labs(
      y = "Proportion of Frames",
      x = "Category",
      title = "Top 50 Objects Across Subjects",
      subtitle = "Percentage of frames containing each object",
      fill = "Mean\nConfidence"
    )
  
  ggsave(here::here("analysis_plots/top50_by_subject_proportions_nolabels.png"),
         p,
         width = 22,
         height = 25)
  
  return(p)
}

# Plot by age - BIGGER labels
plot_top50_by_age_prop <- function() {
  # Get overall top 50 objects
  top50_objects <- get_overall_top50_prop(objects_joined_with_categories)
  
  # Get total frames per age bin
  age_totals <- objects_joined_with_categories %>%
    filter(age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, age_bin) %>%
    group_by(age_bin) %>%
    summarise(total_frames = n())
  
  # Get per-age-bin proportions for these objects
  age_props <- objects_joined_with_categories %>%
    filter(class_name %in% top50_objects,
           age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, age_bin, .keep_all = TRUE) %>%
    group_by(age_bin, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),
      .groups = 'drop'
    ) %>%
    left_join(age_totals, by = "age_bin") %>%
    mutate(proportion = n_occurrences/total_frames) %>%
    complete(age_bin, class_name, 
             fill = list(n_occurrences = 0, 
                        mean_confidence = 0, 
                        n_participants = 0,
                        proportion = 0))
  
  p <- ggplot(age_props, 
              aes(x = reorder(class_name, proportion),
                  y = proportion,
                  fill = mean_confidence)) +
    geom_bar(stat = "identity") +
    facet_wrap(~age_bin) +
    scale_fill_gradient(low = "lightblue", high = "darkblue") +
    scale_y_continuous(labels = scales::percent) +
    coord_flip() +
    theme_few() +
    theme(
      axis.text.y = element_text(hjust = 0, size = 14),
      axis.text.x = element_text(size = 12),
      strip.text = element_text(size = 12),
      plot.title = element_text(size = 12)
    ) +
    labs(
      y = "Proportion of Frames",
      x = "Category",
      title = "Top 50 Objects Across Age Groups",
      subtitle = "Percentage of frames containing each object",
      fill = "Mean\nConfidence"
    )
  
  ggsave(here::here("analysis_plots/top50_by_age_proportions_nolabels.png"),
         p,
         width = 17,
         height = 20)
  
  return(p)
}

# Generate the plots
p2_prop_50 <- plot_top50_by_subject_prop()
p3_prop_50 <- plot_top50_by_age_prop()

# Print summary
print("Category distribution in top 50 (proportional analysis):")
print(table(top50_data_prop$category_type))
```


# Load MCDI-AOA data
```{r}
mcdi_aoa <- read_csv(here::here("MCDI_items_with_AoA.csv"))
```
# Merge the AOA column from MCDI-AOA data with objects_joined_with_categories using uni_lemma column
```{r}
# Merge the AOA data with our objects
objects_joined_with_categories_aoa <- objects_joined_with_categories %>%
  left_join(mcdi_aoa %>% select(uni_lemma, AoA), 
            by = c("class_name" = "uni_lemma"))

# Check the matching
matching_summary <- objects_joined_with_categories_aoa %>%
  group_by(class_name) %>%
  summarise(
    n_occurrences = n(),
    has_aoa = !all(is.na(AoA)),
    aoa_value = first(na.omit(AoA))
  ) %>%
  arrange(desc(n_occurrences))

# Print summary of matches
print("Objects with AoA matches:")
print(matching_summary %>% filter(has_aoa) %>% select(class_name, n_occurrences, aoa_value))

print("\nObjects without AoA matches:")
print(matching_summary %>% filter(!has_aoa) %>% select(class_name, n_occurrences))
```

# New analysis: Comprehensive object detection with AOA
# ==================================================

```{r}
# Get proportions by subject and age bin with specific age ranges
get_detailed_proportions_aoa <- function(data) {
  # First ensure age bins are correctly categorized
  data <- data %>%
    mutate(age_bin = case_when(
      age_mo >= 6 & age_mo < 12 ~ "06-12 months",
      age_mo >= 12 & age_mo < 18 ~ "12-18 months",
      age_mo >= 18 ~ "18-24+ months",
      TRUE ~ "Other"
    ))
  
  # Get total frames per subject-age combination (only for our age bins of interest)
  totals <- data %>%
    filter(age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, subject_id, age_bin) %>%
    group_by(subject_id, age_bin) %>%
    summarise(total_frames = n(), .groups = 'drop')
  
  # Get proportions for all objects by subject and age
  detailed_props <- data %>%
    filter(!class_name %in% c("person", "picture"),
           age_bin %in% c("06-12 months", "12-18 months", "18-24+ months")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, subject_id, age_bin, .keep_all = TRUE) %>%
    group_by(subject_id, age_bin, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    ) %>%
    left_join(totals, by = c("subject_id", "age_bin")) %>%
    mutate(proportion = n_occurrences/total_frames)
  
  return(detailed_props)
}

# Get overall proportions for all categories
get_all_object_proportions_aoa <- function(data) {
  # Get total number of frames
  total_frames <- data %>%
    distinct(superseded_gcp_name_feb25, frame_id) %>%
    nrow()
  
  # Get proportions for all objects
  all_objects <- data %>%
    filter(!class_name %in% c("person", "picture")) %>%
    distinct(superseded_gcp_name_feb25, frame_id, class_name, subject_id, age_bin, .keep_all = TRUE) %>%
    group_by(class_name) %>%
    summarise(
      n_occurrences = n(),
      proportion = n()/total_frames,
      mean_confidence = mean(confidence),
      n_participants = n_distinct(subject_id),
      .groups = 'drop'
    ) %>%
    arrange(desc(proportion))
  
  return(all_objects)
}

# Create comprehensive dataframe with all information
comprehensive_data_aoa <- get_detailed_proportions_aoa(objects_joined_with_categories) %>%
  # Add overall proportions
  left_join(
    get_all_object_proportions_aoa(objects_joined_with_categories) %>%
      select(class_name, overall_proportion = proportion),
    by = "class_name"
  ) %>%
  # Add AoA information
  left_join(
    mcdi_aoa %>% select(uni_lemma, AoA),
    by = c("class_name" = "uni_lemma")
  )

# Look at the data distribution across age bins
print("Data distribution across age bins:")
print(table(comprehensive_data_aoa$age_bin))

# Basic summary by age bin
summary_by_age_aoa <- comprehensive_data_aoa %>%
  group_by(age_bin) %>%
  summarise(
    n_subjects = n_distinct(subject_id),
    n_objects = n_distinct(class_name),
    mean_prop = mean(proportion),
    n_with_aoa = sum(!is.na(AoA))
  )

print("\nSummary by age bin:")
print(summary_by_age_aoa)

# Save the comprehensive data
write_csv(comprehensive_data_aoa, 
          here::here("analysis_plots/comprehensive_object_data_with_aoa.csv"))
```

## Clean up the dataframe with AoA
```{r}
# Remove rows where AoA is NA
comprehensive_data_aoa <- comprehensive_data_aoa %>%
  filter(!is.na(AoA))

# When objects have multiple AoA values, keep the smallest AoA value
comprehensive_data_aoa <- comprehensive_data_aoa %>%
  group_by(class_name) %>%
  mutate(AoA = min(AoA)) %>%
  ungroup()
```

## Plot prop. of detected objects vs. AoA by age bin (without averaging)
```{r}
# Plot 6-12 months
p1 <- comprehensive_data_aoa %>%
  filter(age_bin == "06-12 months") %>%
  ggplot(aes(x = AoA, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_few() +
  labs(x = "AoA", y = "Proportion of detected objects")

# Plot 12-18 months
p2 <- comprehensive_data_aoa %>%
  filter(age_bin == "12-18 months") %>%
  ggplot(aes(x = AoA, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_few() +
  labs(x = "AoA", y = "Proportion of detected objects")       

# Plot 18-24+ months
p3 <- comprehensive_data_aoa %>%
  filter(age_bin == "18-24+ months") %>%
  ggplot(aes(x = AoA, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +  
  theme_few() +
  labs(x = "AoA", y = "Proportion of detected objects")

# Combine the plots
combined_plot <- cowplot::plot_grid(p1, p2, p3, ncol = 3) 

# Save the combined plot
ggsave(here::here("analysis_plots/combined_plot_prop_aoa_by_age.png"), 
       combined_plot, 
       width = 15, 
       height = 5)  
``` 

## Plot prop. of detected objects vs. AoA by age bin (with averaging)
```{r}
# First, calculate mean proportions per object and age bin
age_bin_summary <- comprehensive_data_aoa %>%
  group_by(class_name, age_bin) %>%
  summarise(
    mean_proportion = mean(proportion),
    AoA = first(AoA),
    n_subjects = n_distinct(subject_id),
    .groups = 'drop'
  ) %>%
  filter(!is.na(AoA))  # Only keep objects with AOA values

# Create labels for:
# - Top 5 most frequent objects per age bin
# - Top 5 earliest and latest acquired objects
objects_to_label <- age_bin_summary %>%
  group_by(age_bin) %>%
  filter(
    rank(-mean_proportion) <= 5 |  # most frequent
    rank(AoA) <= 5 |              # earliest acquired
    rank(-AoA) <= 5               # latest acquired
  )

# Calculate correlations for each age bin
correlations <- age_bin_summary %>%
  group_by(age_bin) %>%
  summarise(
    r = cor(mean_proportion, AoA, method = "pearson"),
    p = cor.test(mean_proportion, AoA)$p.value,
    label = sprintf("r = %.2f\np = %.3f", r, p),
    .groups = 'drop'
  )

# Detailed correlation analysis
detailed_correlations <- age_bin_summary %>%
  group_by(age_bin) %>%
  summarise(
    n_objects = n(),
    r = cor(mean_proportion, AoA, method = "pearson"),
    p = cor.test(mean_proportion, AoA)$p.value,
    mean_prop = mean(mean_proportion),
    sd_prop = sd(mean_proportion),
    mean_AOA = mean(AoA),
    sd_AOA = sd(AoA)
  )

# Print detailed results
print("Detailed correlation analysis by age bin:")
print(detailed_correlations, n = Inf)

# Create scatter plots with correlation info
ggplot(age_bin_summary, 
       aes(x = mean_proportion, y = AoA)) +
  geom_smooth(method = "lm", 
             color = "blue",
             alpha = 0.2) +
  geom_point(alpha = 0.5) +
  geom_label_repel(
    data = objects_to_label,
    aes(label = class_name),
    size = 3,
    box.padding = 0.5,
    point.padding = 0.3,
    force = 10,
    max.overlaps = 20,
    direction = "both"
  ) +
  # Add detailed correlation text
  geom_text(
    data = detailed_correlations,
    aes(label = sprintf(
      "n = %d\nr = %.3f\np = %.3e\nmean prop = %.3f\nmean AOA = %.1f",
      n_objects, r, p, mean_prop, mean_AOA
    )),
    x = 0.01,
    y = 35,
    hjust = 0,
    vjust = 1
  ) +
  facet_wrap(~age_bin, ncol = 1) +
  theme_few() +
  scale_x_continuous(labels = scales::percent) +
  labs(
    x = "Proportion of Frames",
    y = "Age of Acquisition (months)",
    title = "Object Detection Frequency vs Age of Acquisition by Age Group",
    subtitle = "Labels shown for most frequent and extreme AOA objects\nBlue line shows linear fit with 95% confidence interval"
  ) +
  theme(
    strip.text = element_text(size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

ggsave(here::here("analysis_plots/aoa_vs_proportion_by_age_labeled_with_lm_detailed.png"),
       width = 12,
       height = 15)
```

```{r}
# Calculate overall mean proportions per object
overall_summary <- comprehensive_data_aoa %>%
  group_by(class_name) %>%
  summarise(
    mean_proportion = mean(proportion),
    AoA = first(AoA),
    n_subjects = n_distinct(subject_id),
    .groups = 'drop'
  ) %>%
  filter(!is.na(AoA))  # Only keep objects with AoA values

# Identify objects to label (top frequent and extreme AoA)
objects_to_label <- overall_summary %>%
  filter(
    rank(-mean_proportion) <= 5 |  # most frequent
    rank(AoA) <= 5 |              # earliest acquired
    rank(-AoA) <= 5               # latest acquired
  )

# Create the plot
ggplot(overall_summary, 
       aes(x = mean_proportion, y = AoA)) +
  geom_smooth(method = "lm", 
             color = "blue",
             alpha = 0.2) +
  geom_point(alpha = 0.5) +
  geom_label_repel(
    data = objects_to_label,
    aes(label = class_name),
    size = 3,
    box.padding = 0.5,
    point.padding = 0.3,
    force = 10,
    max.overlaps = 20,
    direction = "both"
  ) +
  theme_few() +
  scale_x_continuous(labels = scales::percent) +
  labs(
    x = "Mean Proportion of Frames",
    y = "Age of Acquisition (months)",
    title = "Object Detection Frequency vs Age of Acquisition",
    subtitle = "Labels shown for most frequent and extreme AoA objects\nBlue line shows linear fit with 95% confidence interval"
  )

# Calculate and print correlation
cor_test <- cor.test(overall_summary$mean_proportion, overall_summary$AoA)
print(paste("Correlation:", round(cor_test$estimate, 3)))
print(paste("P-value:", format.pval(cor_test$p.value, digits = 3)))

ggsave(here::here("analysis_plots/aoa_vs_proportion_overall_vertical.png"),
       width = 6,
       height = 15)
```

# Check for zero detections
```{r}
# Find instances of zero detections
zero_detections <- comprehensive_data_aoa %>%
  filter(proportion == 0) %>%
  select(class_name, subject_id, age_bin, proportion, AoA) %>%
  arrange(class_name, subject_id)

# Summary statistics of zero detections
zero_summary <- zero_detections %>%
  group_by(class_name) %>%
  summarise(
    n_zero_instances = n(),
    n_subjects = n_distinct(subject_id),
    age_bins = paste(unique(age_bin), collapse = ", "),
    AoA = first(AoA)
  ) %>%
  arrange(desc(n_zero_instances))

# Print summaries
print("Summary of objects with zero detections:")
print(zero_summary, n = Inf)

print("\nNumber of zero detections by age bin:")
print(table(zero_detections$age_bin))

print("\nNumber of zero detections by subject:")
print(table(zero_detections$subject_id))

# Save detailed results to a file
write.csv(zero_detections, 
          here::here("analysis_plots/zero_detections_details.csv"), 
          row.names = FALSE)

write.csv(zero_summary, 
          here::here("analysis_plots/zero_detections_summary.csv"), 
          row.names = FALSE)
```

```{r}
# Prepare scaled data
model_data <- comprehensive_data_aoa %>%
  mutate(
    proportion_scaled = scale(proportion)[,1],
    total_frames_scaled = scale(total_frames)[,1],
    AoA_scaled = scale(AoA)[,1],
    age_bin = factor(age_bin, levels = c("06-12 months", "12-18 months", "18-24+ months")),
    age_numeric = as.numeric(age_bin)
  )

# First model: proportion as outcome -- does frequency change across age? across individual subjects?
mixed_model_1 <- lmer(
  proportion_scaled ~ scale(age_numeric) + total_frames_scaled + 
    (age_numeric |subject_id) + (1|class_name), 
  data = model_data,
  control = lmerControl(optimizer = "bobyqa")
)

```

```{r}
model_data_averaged <- model_data %>%
  group_by(class_name, subject_id, AoA_scaled) %>%
  summarize(mean_proportion = mean(proportion_scaled), total_frames_by_sub = sum(total_frames))

# Second model: AoA as outcome, does category frequency change across age?
mixed_model_2 <- lmer(
  AoA_scaled ~ mean_proportion  + scale(total_frames_by_sub)[,1] + 
    (1|subject_id) + (1|class_name), 
  data = model_data_averaged,
  control = lmerControl(optimizer = "bobyqa")
)

# Print summaries
cat("\nModel 1 (Proportion as outcome):\n")
print(summary(mixed_model_1))

cat("\nModel 2 (AoA as outcome):\n")
print(summary(mixed_model_2))
```

```{r}
# Get confidence intervals for both models
cat("\nConfidence Intervals for Model 1:\n")
print(confint(mixed_model_1, method = "boot", nsim = 1000))

cat("\nConfidence Intervals for Model 2:\n")
print(confint(mixed_model_2, method = "boot", nsim = 1000))

# Create effects plots for both models
library(effects)
par(mfrow = c(2,1))
plot(allEffects(mixed_model_1), main = "Model 1: Effects on Proportion")
plot(allEffects(mixed_model_2), main = "Model 2: Effects on AoA")

# Back-transform estimates to original scale for both models
coef_summary_1 <- data.frame(summary(mixed_model_1)$coefficients)
coef_summary_1$original_scale <- coef_summary_1$Estimate * sd(model_data$proportion) + mean(model_data$proportion)

coef_summary_2 <- data.frame(summary(mixed_model_2)$coefficients)
coef_summary_2$original_scale <- coef_summary_2$Estimate * sd(model_data$AoA) + mean(model_data$AoA)

cat("\nModel 1 coefficients (back-transformed):\n")
print(coef_summary_1)

cat("\nModel 2 coefficients (back-transformed):\n")
print(coef_summary_2)
```

```{r}
get_detailed_proportions_by_month_aoa <- function() {
  # Calculate total frames per subject-month combination
  frames_per_subject_month <- objects_joined_with_categories %>%
    distinct(frame_id, subject_id, age_mo) %>%
    group_by(subject_id, age_mo) %>%
    summarise(
      total_frames = n(),
      .groups = 'drop'
    )
  
  # Get object occurrences by subject and month
  object_occurrences <- objects_joined_with_categories %>%
    filter(!class_name %in% c("person", "picture")) %>%
    group_by(subject_id, age_mo, class_name) %>%
    summarise(
      n_occurrences = n(),
      mean_confidence = mean(confidence),
      .groups = 'drop'
    )
  
  # Join with total frames and calculate proportions
  detailed_props <- object_occurrences %>%
    left_join(frames_per_subject_month, by = c("subject_id", "age_mo")) %>%
    mutate(proportion = n_occurrences / total_frames)
  
  # Get overall proportions across all subjects and months
  overall_props <- get_all_object_proportions_aoa()
  
  # Join with AoA data
  comprehensive_data <- detailed_props %>%
    left_join(overall_props, by = "class_name") %>%
    left_join(
      mcdi_aoa %>% select(uni_lemma, AoA),
      by = c("class_name" = "uni_lemma")
    )
  
  # Print summary of data distribution
  cat("\nData distribution across months:\n")
  print(table(comprehensive_data$age_mo))
  
  # Print summary by month
  month_summary <- comprehensive_data %>%
    group_by(age_mo) %>%
    summarise(
      n_subjects = n_distinct(subject_id),
      n_objects = n_distinct(class_name),
      mean_prop = mean(proportion),
      n_with_aoa = sum(!is.na(AoA))
    )
  
  cat("\nSummary by month:\n")
  print(month_summary)
  
  # Save to CSV
  write.csv(
    comprehensive_data,
    here::here("analysis_plots/comprehensive_object_data_by_month.csv"),
    row.names = FALSE
  )
  
  return(comprehensive_data)
}
```

```{r}
# Calculate overall proportions for each category
overall_category_distribution <- objects_joined_with_categories %>%
  # First get total number of frame-video-subject-age combinations
  ungroup() %>%
  distinct(frame_id, superseded_gcp_name_feb25, subject_id, age_mo) %>%
  summarise(total_frame_video_subject_age_combinations = n()) %>%
  # Then join with object counts
  cross_join(
    objects_joined_with_categories %>%
      # Count unique frame-video-subject-age combinations for each object
      # Using distinct to count each object only once per frame
      distinct(class_name, frame_id, superseded_gcp_name_feb25, subject_id, age_mo, .keep_all = TRUE) %>%
      group_by(class_name) %>%
      summarise(
        n_frame_video_subject_age_detections = n(),
        n_unique_videos = n_distinct(superseded_gcp_name_feb25),
        n_subjects = n_distinct(subject_id),
        n_ages = n_distinct(age_mo),
        mean_confidence = mean(confidence)  # moved confidence calculation here
      )
  ) %>%
  # Calculate proportion
  mutate(
    proportion = n_frame_video_subject_age_detections / total_frame_video_subject_age_combinations
  ) %>%
  # Join with AoA data
  left_join(
    mcdi_aoa %>% select(uni_lemma, AoA),
    by = c("class_name" = "uni_lemma")
  ) %>%
  # Select and arrange columns in desired order
  select(
    class_name,
    n_frame_video_subject_age_detections,   # Number of frame-video-subject-age combinations
    n_unique_videos,                        # Number of unique videos
    total_frame_video_subject_age_combinations,  # Total frame-video-subject-age combinations
    proportion,                             # Proportion of frame-video-subject-age combinations
    n_subjects,                             # Number of subjects
    n_ages,                                 # Number of unique ages
    mean_confidence,
    AoA
  ) %>%
  # Arrange by proportion in descending order
  arrange(desc(proportion))

# Print summary
print("Top 20 most frequently detected objects:")
print(
  overall_category_distribution %>%
    select(class_name, n_frame_video_subject_age_detections,
           n_unique_videos, total_frame_video_subject_age_combinations, 
           proportion, n_subjects, n_ages, AoA) %>%
    head(20)
)

# Save to CSV
write.csv(
  overall_category_distribution,
  here::here("analysis_plots/overall_category_distribution.csv"),
  row.names = FALSE
)

# Diagnostic counts
cat("\nDiagnostic Counts:\n")
cat("------------------\n")
diagnostics <- objects_joined_with_categories %>%
  summarise(
    total_frames = n_distinct(frame_id),
    total_videos = n_distinct(superseded_gcp_name_feb25),
    total_subjects = n_distinct(subject_id),
    total_ages = n_distinct(age_mo)
  )
print(diagnostics)
```
